### 2020-08-08 outputs/documents/paper.Rmd
Add skeleton of paper.

---
title: "Notes and approaches to OCR"
author: "Rohan Alexander, John Tang, Diego Mamanche Castellanos"
date: "08 August 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

A crucial aspect of the data science workflow is gathering data...

The Portable Document Format (PDF) is widely used for documents that ...

However, this advantage means that the data in PDFs cannot be used for quantitiative statistical analysis...

Sometimes you can just copy paste....

But other times it's an image....

Hence, optical character recognition (OCR)...

In this paper we review various OCR options for researchers who need to gather data from PDFs that must be OCR....

When they consider a primer on what OCR options exist these days depending on your technical ability and then how they perform for an easy example and then how they perform for a hard example (the Japanese extract) and finally some suggestions for what is needed in the future....

Our paper represents...

The remainder of this paper is structured as follows...

# Data

## OCR options

**(Diego: please add options here in a table and then a brief write-up of each - costs, access, technical requirements, etc.)**

## Test samples

Japanese dictionaries...

# Evaluation

For each option, we rank them based on two scales: results and difficulty. We need to work out a definition for each of these.

The main aspect of the end product will be a graph with two axis, and dots for where each service is positioned, coloured or faceted by the test.

# Discussion

# References

### 2020-08-08 scripts/focus_on_a.R

@@ -1,0 +1,136 @@
+library(tidyverse)
+
+a <- read_lines("outputs/01_after_ocr/01-a.ocr.txt")
+
+
+a <- tibble(raw = a, letter = "a")
+
+# Clean up some brackets
+a <- 
+  a %>% 
+  mutate(raw = str_replace_all(raw, "〔", " ["),
+         raw = str_replace_all(raw, "〔", " [")) %>% 
+  mutate(raw = str_replace_all(raw, "〕", "] "),
+         raw = str_replace_all(raw, "】", "] ")) %>% 
+  mutate(raw = str_replace_all(raw, "〔", " ["),
+         raw = str_replace_all(raw, "【", " ["),
+         raw = str_replace_all(raw, "〖", " [")
+  )
+
+
+# Change the following to "ア|"
+all <- 
+  all %>% 
+  mutate(raw = str_replace_all(raw, "ア1", "ア—"),
+         raw = str_replace_all(raw, "ア1", "ア—"),
+  )
+
+# Sometimes they are small
+all <- 
+  all %>% 
+  mutate(raw = str_replace_all(raw, "ァ", "ア"),
+         raw = str_replace_all(raw, "ぃ", "い"),
+         raw = str_replace_all(raw, "ぅ", "う"),
+  )
+
+
+write_csv(a, "test.csv")
+
+
+start <- sample(x = c(1:nrow(all)), size = 1)
+all[start:(start+15),]
+
+rm(start)
+
+# Talk to John:
+# For a: line 3070, there is some weird: "あ9" thing - 9 should be "り"
+# For i: line 3044, there is some weird: "い9" thing
+
+
+
+# a is あ or ア
+# i is い or イ
+# u is う or ヴ or ウ
+# e is え or エ
+# o is お or 才
+
+
+# Add flag for if the line starts with  "あ" or "ア"
+a <- 
+  all %>% 
+  filter(letter == "a") %>% 
+  mutate(start_of_a_definition = if_else(str_starts(raw, "あ"), 1, 0),
+         start_of_a_definition = if_else(str_starts(raw, "ア"), 1, start_of_a_definition),
+         ) %>% 
+  mutate(word_counts = cumsum(start_of_a_definition)) %>% 
+  group_by(word_counts) %>%
+  summarise(words=paste(raw,collapse='')) %>% 
+  select(-word_counts) %>% 
+  mutate(letter = "a")
+
+i <- 
+  all %>% 
+  filter(letter == "i") %>% 
[…]

### 2020-08-08 scripts/have_a_go.R

@@ -6,9 +6,11 @@ library(tesseract)
 # https://cran.r-project.org/web/packages/tesseract/vignettes/intro.html
 
 
-pngfile <- pdftools::pdf_convert('inputs/Sample dictionary pages.pdf', dpi = 600)
+pngfile <- ?pdftools::pdf_convert('inputs/00-sample dictionary pages.pdf', dpi = 600)
 
 pngfile[1]
+
+pngfile <- 
 
 tesseract_info()
 
@@ -24,16 +26,16 @@ tesseract_download("jpn_vert")
 japanese_vertical <- tesseract("jpn_vert")
 
 
-text <- ocr("top_row_of_first_page.png", engine = japanese_vertical)
+text <- ocr("inputs/a.png", engine = japanese_vertical)
 
 
 english_and_japanese <- tesseract("eng+jpn_vert")
 
 # Try pre-processing a bit more
 library(magick)
-image_read(pngfile[1]) %>% 
+image_read("inputs/a.png") %>% 
   # image_info()
-  image_crop("1700x1050+300+270") %>% 
+  # image_crop("1700x1050+300+270") %>% 
   image_convert(colorspace = 'gray') %>%
   image_trim() %>% 
   # image_scale("x2000") %>% 

### 2020-08-12 outputs/documents/paper.Rmd
Include OCR tools in a table

@@
 
-**(Diego: please add options here in a table and then a brief write-up of each - costs, access, technical requirements, etc.)**
+| OCR Tool                             | Company	 | Type           |	Pricing |	Tech Requierements |
+| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
+| Azure Cognitive Services (OCR)       | Microsoft | API		        |         |                    |
+| Amazon Rekognition	                 | Amazon	   | API		        |         |                    |
+| Tesseract		                         |           | R library      | Free	  |                    |
+| OpenCV		                           |           | Python Library | Free	  |                    |
+| Watson Visual Recognition	           | IBM	     | API		        |         |                    |
+| Kraken		                           |           | Python Library	| Free	  |                    |
+| Google Vision (for Text recognition) | Google	   | API		        |         |                    |
+| SwiftOCR	(iOS)                      | Apple	   | Swift Library  |         |                    | 		
+| Amazon Textract	                     | Amazon	   | API		        |         |                    |
+|	Tensorflow                           | Google    | Python Library | Free    |                    |
 

### 2020-08-17 outputs/documents/paper.Rmd
Add PyTesseract to the list

--- 2020-08-08 outputs/documents/paper.Rmd
@@
 
-**(Diego: please add options here in a table and then a brief write-up of each - costs, access, technical requirements, etc.)**
+| OCR Tool                             | Company	 | Type           |	Pricing |	Tech Requierements |
+| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
+| Azure Cognitive Services (OCR)       | Microsoft | API		        |         |                    |
+| Amazon Rekognition	                 | Amazon	   | API		        |         |                    |
+| Tesseract		                         |           | R library      | Free	  |                    |
+| PyTesseract                          |           | Python Library | Free    |                    |
+| OpenCV		                           |           | Python Library | Free	  |                    |
+| Watson Visual Recognition	           | IBM	     | API		        |         |                    |
+| Kraken		                           |           | Python Library	| Free	  |                    |
+| Google Vision (for Text recognition) | Google	   | API		        |         |                    |
+| SwiftOCR	(iOS)                      | Apple	   | Swift Library  |         |                    | 		
+| Amazon Textract	                     | Amazon	   | API		        |         |                    |
+|	Tensorflow                           | Google    | Python Library | Free    |                    |
 

### 2020-08-17 outputs/documents/paper.Rmd
Add PyTesseract Library to the list

--- 2020-08-08 outputs/documents/paper.Rmd
@@
 
-**(Diego: please add options here in a table and then a brief write-up of each - costs, access, technical requirements, etc.)**
+| OCR Tool                             | Company	 | Type           |	Pricing |	Tech Requierements |
+| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
+| Azure Cognitive Services (OCR)       | Microsoft | API		        |         |                    |
+| Amazon Rekognition	                 | Amazon	   | API		        |         |                    |
+| Tesseract		                         |           | R library      | Free	  |                    |
+| PyTesseract (Wrapper Google's OCR Engine)    |           | Python Library | Free    |                    |
+| OpenCV		                           |           | Python Library | Free	  |                    |
+| Watson Visual Recognition	           | IBM	     | API		        |         |                    |
+| Kraken		                           |           | Python Library	| Free	  |                    |
+| Google Vision (for Text recognition) | Google	   | API		        |         |                    |
+| SwiftOCR	(iOS)                      | Apple	   | Swift Library  |         |                    | 		
+| Amazon Textract	                     | Amazon	   | API		        |         |                    |
+|	Tensorflow                           | Google    | Python Library | Free    |                    |
 

### 2020-08-19 outputs/documents/paper.Rmd
Clarify that Kraken only runs on Linux OS

--- 2020-08-12 outputs/documents/paper.Rmd
@@
 | Tesseract		                         |           | R library      | Free	  |                    |
+| PyTesseract (Wrapper Google's OCR Engine)    |           | Python Library | Free    |                    |
 | OpenCV		                           |           | Python Library | Free	  |                    |
 | Watson Visual Recognition	           | IBM	     | API		        |         |                    |
-| Kraken		                           |           | Python Library	| Free	  |                    |
+| Kraken	(Linux OS)                   |           | Python Library	| Free	  |                    |
 | Google Vision (for Text recognition) | Google	   | API		        |         |                    |
@@
 
+Diego's comment: From what I learned so far, it could be easiness (an API is more straightforward than a library), number of characters correctly recognized, flexibility (the opposite of easiness), and cost.
+Moreover, some APIs such as Google's groups more than one character, whereas Azure returns only one character per boundary.
+
 The main aspect of the end product will be a graph with two axis, and dots for where each service is positioned, coloured or faceted by the test.

### 2020-08-24 outputs/documents/paper.Rmd
Introduction draft and API costs

@@
 
-A crucial aspect of the data science workflow is gathering data...
+A crucial aspect of the data science workflow is gathering data.
+It involves the tools and methods used to collect information in an established systematic fashion and identify the variables being measured.
+It also describes the methods used to obtain the data.
+Although the data collection component of research remains the same regardless of the field of study, the methods used vary among those fields of study as they have different interests.
+Moreover, the diversity of data types adds complexity to the process of gathering data.
+Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset.
+Some examples are tables and relations.
+Semi-structured data contains this same information, but instead of having regular structures applied to all items in the dataset, the data might be interpreted with structural information.
+It can be supplied as tags e.g.
+name = "Bob" but also other markers to separate semantic elements and enforce hierarchies of records and fields within the data.
+Finally, Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags.
+However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data (Robert M.
+Losee, 2005).
+This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.
 
-The Portable Document Format (PDF) is widely used for documents that ...
+The Portable Document Format (PDF) is an example of unstructured data created by the company Adobe in the 90s.
+It is widely used for documents.
+According to the ISO 32000-2:2017, the latest edition of the PDF Reference (2.0), PDF enables users to exchange and view electronic documents easily and reliably, independent of the environment in which they were created or the environment in which they are viewed or printed.
+It is intended to fulfill the following requirements:
 
-However, this advantage means that the data in PDFs cannot be used for quantitiative statistical analysis...
+- preservation of document fidelity independent of the device, platform, and software,
+- merging of content from diverse sources — Web sites, word processing and spreadsheet
+programs, scanned documents, photos, and graphics — into one self-contained document while
+maintaining the integrity of all original source documents,
+- an extensible metadata model at the document and object level,
+- collaborative editing of documents from multiple locations or platforms,
+- digital signatures to certify authenticity,
+- security and permissions to allow the creator to retain control of the document and associated
+rights,
+- accessibility of content to those with disabilities,
+- extraction and reuse of content for use with other file formats and applications, and
+- electronic forms to gather and/or represent data within business systems.
 
-Sometimes you can just copy paste....
+To mention some of the features incorporated in this version we have:
 
-But other times it's an image....
+- 12.10, "Geospatial features";
+- 13.7, "Rich media" annotations;
+- 14.7.4, "Namespaces" for tagged PDF;
+- 14.9.6, "Pronunciation hints";
+- 14.12, "Document parts";
+- 14.13, "Associated files";
+- Support for PRC (see 13.6, "3D Artwork");
+- Support for UTF-8.
 
-Hence, optical character recognition (OCR)...
+However, these advantages mean that the data in PDFs cannot be used for quantitative statistical analysis.
+The reason is that it needs measurable and verifiable data.
+But PDF documents, as it was mentioned previously, can have different objects, some of them non-static objects compressed in the same document.
+This situation makes it difficult to extract valuable information from the paper.
 
-In this paper we review various OCR options for researchers who need to gather data from PDFs that must be OCR....
+Sometimes just by copying and pasting the information directly from the PDF is possible when it contains simple texts or regular tables.
+In that case, there is no barrier in the process of extracting data.
+But other times it is not as easy if it is an image, a survey form, or complex shapes containing relevant information, .
+Furthermore, there is a linguistic component that adds more complexity.
+For instance, it is well known that non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process.
+It is because those characters have complicated structures, a huge number of categories, and resemblance among characters, font unevenness, or writing styles.
+In those cases, the need for reliable tools or methods with the ability to elicit data becomes extremely important.
 
-When they consider a primer on what OCR options exist these days depending on your technical ability and then how they perform for an easy example and then how they perform for a hard example (the Japanese extract) and finally some suggestions for what is needed in the future....
+Optical character recognition (OCR), a process that transforms a bitmapped image of printed or handwritten text into text code, and thereby making it machine-readable, has been widely used for scientists trying to capture the images of characters and texts back in the 50s.
+First, by mechanical and optical means of rotating disks and photomultiplier flying spot scanner with a cathode ray tube lens, followed by photocells and arrays of them.
+The OCR process was slow, and one line of characters could be digitized at a time.
+Nowadays, in OCR, once a printed or handwritten text has been captured optically by a scanner or some other optical means, the digital image goes through the following stages of a computer recognition system (Cheriet, Mohamed; Kharma, 2007):
 
-Our paper represents...
+- The preprocessing stage that enhances the quality of the input image and locates
+the data of interest.
+- The feature extraction stage that captures the distinctive characteristics of the
+digitized characters for recognition.
+- The classification stage that processes the feature vectors to identify the characters and words.
 
-The remainder of this paper is structured as follows...
+In this paper we review various OCR options for researchers who need to gather data from PDFs in which the text must be extracted to be reused, edited, or reformatted; the text should be available for full-text information retrieval; the text is to be coded in HTML or SGML; the text should be available to adaptive equipment for the visually impaired; the file size is of concern (in terms of storage or bandwidth to transmit); or the resources are available to perform OCR and correct the output.
+
+**When they consider a primer on what OCR options exist these days depending on your technical ability and then how they perform for an easy example and then how they perform for a hard example (the Japanese extract) and finally some suggestions for what is needed in the future....**
+
+**Our paper represents...**
+
+**The remainder of this paper is structured as follows...**
 
@@
 
-| OCR Tool                             | Company	 | Type           |	Pricing |	Tech Requierements |
+| OCR Tool                             | Company	 | Type           |	Monthly Price Aug/2020 |	Tech Requierements |
 | ------------------------------------ | --------- | -------------- | ------- | ------------------ |
-| Azure Cognitive Services (OCR)       | Microsoft | API		        |         |                    |
-| Amazon Rekognition	                 | Amazon	   | API		        |         |                    |
+| Azure Cognitive Services (OCR)       | Microsoft | API		        | Free Web Container: 5000/Free; <br/> <br/> S1 Web Container: 0-1M/$1.50 per 1,000 trans, 1M-5M/$1 per 1,000 trans, 5M-10M/$0.65 per 1,000 trans, 10M-100M/$0.65 per 1,000 trans, +100M/$0.65 per 1,000 trans        |                    |
+| Amazon Rekognition	                 | Amazon	   | API		        | First 1 million images: $0.001 per image <br/> <br/> Next 9 million images $0.0008 per image <br/> <br/> Next 90 million images $0.0006 per image <br/> <br/> Over 100 million images $0.0004 per image         |                    |
 | Tesseract		                         |           | R library      | Free	  |                    |
@@
 | OpenCV		                           |           | Python Library | Free	  |                    |
-| Watson Visual Recognition	           | IBM	     | API		        |         |                    |
+| Watson Visual Recognition	           | IBM	     | API		        | Lite: 1000/Free, <br/> <br/> Standard: $0.002 per trans      |                    |
 | Kraken	(Linux OS)                   |           | Python Library	| Free	  |                    |
-| Google Vision (for Text recognition) | Google	   | API		        |         |                    |
+| Google Vision (for Text recognition) | Google	   | API		        | 1000/Free, 5 mill/$1.5, >5mill/$0.6        |                    |
 | SwiftOCR	(iOS)                      | Apple	   | Swift Library  |         |                    | 		
-| Amazon Textract	                     | Amazon	   | API		        |         |                    |
+| Amazon Textract	                     | Amazon	   | API		        | First 1 Million pages: $0.015 - $0.05 per page, <br/> <br/> Over 1 Million pages: $0.01 - $0.04 per page        |                    |
 |	Tensorflow                           | Google    | Python Library | Free    |                    |
@@
 # References
+
+https://books-scholarsportal-info.myaccess.library.utoronto.ca/en/read?id=/ebooks/ebooks2/wiley/2011-12-13/1/9780470176535
+
+https://www.researchgate.net/publication/267465115_An_Overview_and_Applications_of_Optical_Character_Recognition

### 2020-09-02 outputs/documents/paper.Rmd
Azure's findings

@@
 date: "08 August 2020"
-output: html_document
+output:
+  pdf_document:
+    latex_engine: xelatex
+  html_document: default
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+
+```
+
+```{r echo=FALSE}
+library("reticulate")
 ```
@@
 Finally, Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags.
-However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data (Robert M.
-Losee, 2005).
+However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data $(Robert M.
+Losee, 2005)^1$.
 This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.
@@
 It is widely used for documents.
-According to the ISO 32000-2:2017, the latest edition of the PDF Reference (2.0), PDF enables users to exchange and view electronic documents easily and reliably, independent of the environment in which they were created or the environment in which they are viewed or printed.
+According to the $ISO 32000-2:2017^2$, the latest edition of the PDF Reference (2.0), PDF enables users to exchange and view electronic documents easily and reliably, independent of the environment in which they were created or the environment in which they are viewed or printed.
 It is intended to fulfill the following requirements:
@@
 The OCR process was slow, and one line of characters could be digitized at a time.
-Nowadays, in OCR, once a printed or handwritten text has been captured optically by a scanner or some other optical means, the digital image goes through the following stages of a computer recognition system (Cheriet, Mohamed; Kharma, 2007):
+Nowadays, in OCR, once a printed or handwritten text has been captured optically by a scanner or some other optical means, the digital image goes through the following stages of a computer recognition system $(Cheriet, Mohamed; Kharma, 2007)^3$:
 
@@
 
+## Test Samples
+
+Japanese dictionaries...
+
 ## OCR options
+
+The following list contains some of the OCR APIs and libraries available that will be evaluated in this study:
 
@@
 
-## Test samples
+## Azure Corgnitive Services - Computer Vision OCR
 
-Japanese dictionaries...
+Among the Microsoft Azure's portfolio, Azure Cognitive Services offers Computer Vision, an API that processes images and returns information based on the visual features the user is interested in.
+Those services comprise object detection of an image, visual features tagging, image categorization, Optical Character Recognition (OCR), among $others^4$.
+The OCR API processes an image and returns the language of the document, orientation, regions, lines, and finally, the characters.
+
+In python we need several libraries for calling the API.
+
+```{python}
+import os
+import sys
+import requests
+# If you are using a Jupyter notebook, uncomment the following line.
+#%matplotlib inline
+import matplotlib.pyplot as plt
+from matplotlib.patches import Rectangle
+from PIL import Image
+from io import BytesIO
+import matplotlib
+import matplotlib.font_manager as font_manager
+from os import path
+import ast
+```
+
+Then, we need to create headers and parameters necessary for calling the API.
+The library **requests** is commonly used in python to do that.
+The method **post** is needed as the API uses the HTTP method POST.
+
+```{python eval=FALSE, include=TRUE}
+#Create the URL for the API call. The endpoint corresponds to the Azure's 
+# endpoint of the account.
+ocr_url = endpoint + "vision/v3.0/ocr"
+
+#Create the header using the Azure's subscription key.
+headers = {'Ocp-Apim-Subscription-Key': subscription_key}
+
+#In params language': 'ja' for japanese only. 'unk' means self detection 
+params = {'language': 'unk', 'detectOrientation': 'true'} 
+data = {'url': image_url}
+
+#Call and save the response using the method post from the library request
+response = requests.post(ocr_url, headers=headers, params=params, json=data)
+
+```
+
+Here we have an example of the response:
+
+```{} 
+{'language': 'ja',
+ 'textAngle': 0.0,
+ 'orientation': 'Up',
+ 'regions': [{'boundingBox': '31,30,1521,2721',
+   'lines': [{'boundingBox': '730,30,44,2718',
+     'words': [{'boundingBox': '735,30,34,34', 'text': 'あ'},
+      {'boundingBox': '736,71,34,26', 'text': 'い'},
+      {'boundingBox': '749,100,6,11', 'text': '・'},
+      {'boundingBox': '735,116,34,27', 'text': 'い'},
+      {'boundingBox': '736,149,33,33', 'text': 'ん'},
+```
+
+### Language and Orientation
+
+Figure 1 presents a sample that corresponds to a Japanese text, but it also contains English text in some fragments of the text.
+The API offers the possibility to do self-detection, which in this case is helpful, but also the opportunity to specify the language in advance.
+Moreover, the orientation can also be self-detected or not.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure1.png)
+**Figure 1**
+
+### Regions
+
+The blue line figure 2 denotes the segment from the image that includes the characters.
+In this example, there is only one blue line because the document is only text.
+In other cases, it may contain images requiring more than one region.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure2.png)
+ **Figure 2**
+
+### Lines
+
+Once the region is defined, the API provides in figure 3 (red rectangles) the subsets of characters of the region called Lines.
+From the example, we can see that some characters are not included in any of the lines.
+Those characters are not recognized by the API.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure3.png)   
+ **Figure 3**
+
+### The Character Boundaries
+
+After the lines are identified, the API provides in figure 4 each recognized character bounding boxes. Those without a yellow square were not recognized by the API in this example.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure4.png)
+ **Figure 4**
+
+### Characters
+
+Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure 5.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure5.png)
+ **Figure 5**
+
+### Advantages and Disadvantages
+
+#### Advantages
+
+The API is easy to use after reading the documentation.
+It offers an example of how to use it in different programming languages.
+It also offers the possibility to self-detect languages and the orientation of the document.
+The response is clear, and extract the information from the JSON file is not complicated.
+
+#### Disadvantages
+
+Even though the API offers the possibility to self-detect the language, It changes the order in which the characters should be in the output.
+In figures 6 we can see that the first line provided by the self-detection approach is located in the middle.
+This situation does not allow a correct interpretation of the text because it does not follow the reading pattern.
+In this case, it is a vertical orientation, which means we have to read it from right to left.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure6.png)
+ **Figure 6**
+
+When the parameter language is stated as Japanese since the beginning, as we can see in figure 7, it recognizes the first line correctly.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure7.png)
+ **Figure 7**
+
+In general, self-detection and the case with the language parameter as the Japanese do not generate the boundaries correctly.
+In Figures 6 and 7, we can observe that both cross the line, which is not correct for in this document.
+There is a line delimiting the boundaries of the text, but it has been ignored by both API calls.
+This situation makes it difficult for researchers to organize the information correctly as the order of the characters matter.
+
+### Future Analysis
+
+By doing some image preprocessing before the API call, it might be possible to see improvements in terms of boundary identification....
+
+## PyTesseract - Python Library
 
@@
 
-https://books-scholarsportal-info.myaccess.library.utoronto.ca/en/read?id=/ebooks/ebooks2/wiley/2011-12-13/1/9780470176535
+1: https://www.researchgate.net/publication/267465115_An_Overview_and_Applications_of_Optical_Character_Recognition
 
-https://www.researchgate.net/publication/267465115_An_Overview_and_Applications_of_Optical_Character_Recognition
+2: https://books-scholarsportal-info.myaccess.library.utoronto.ca/en/read?id=/ebooks/ebooks2/wiley/2011-12-13/1/9780470176535
+
+3:
+
+4: https://docs.microsoft.com/en-us/azure/cognitive-services/computer-vision/home
+
+5: https://docs.microsoft.com/en-us/azure/cognitive-services/computer-vision/quickstarts/python-print-text

### 2020-09-03 outputs/documents/paper.Rmd
Include validation of Google API

@@
 
-```{r echo=FALSE}
+```{r echo=FALSE, include=FALSE, warning=FALSE}
 library("reticulate")
@@
 
-```{python}
+```{python eval=FALSE, include=TRUE}
 import os
@@
 import matplotlib
-import matplotlib.font_manager as font_manager
 from os import path
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure1.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure1_full.png)
 **Figure 1**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure2.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure2_full.png)
  **Figure 2**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure3.png)   
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure3_full.png)   
  **Figure 3**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure4.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure4_full.png)
  **Figure 4**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure5.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure5_full.png)
  **Figure 5**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure6.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure6_full.png)
  **Figure 6**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure7.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure7_full.png)
  **Figure 7**
@@
 By doing some image preprocessing before the API call, it might be possible to see improvements in terms of boundary identification....
+
+## Google Vision OCR
+
+Google Vision API can integrate vision detection features, including image labeling, face and landmark detection, optical character recognition (OCR), and tagging of explicit content.
+The text recognition process detects text in images and recognizes the text contained therein.
+Once detected, the recognizer then determines the actual text in each block and segments it into lines and words.
+
+To evaluate this OCR option, we need the following python libraries.
+
+```{python eval=FALSE, include=TRUE}
+from os import path
+from PIL import Image
+from PIL import ImageFont
+from PIL import ImageDraw
+from PIL import ImageEnhance
+import base64 #Convert an image into base64 form for API requests
+import requests #API request - GET/POST
+import json
+import ast
+```
+
+Same as the Azure API, we need to create the headers and parameters necessary for calling the API.
+We also need the python library **requests** to make the API call.
+The method **post** is needed as the API uses the HTTP method POST.
+
+The following example illustrates how to state the headers and parameter, but also create two functions.
+The first one, called encode_image converts an image into base64, an encoding process designed to carry data stored in binary formats across channels that only reliably support text content.
+It can embed image files or other binary assets inside textual assets.
+The second one makes an HTTP POST request that calls Google's Vision API.
+
+```{python eval=FALSE, include=TRUE}
+#Create the URL for the API call. The endpoint corresponds to the Azure's 
+# endpoint of the account.
+url = "https://vision.googleapis.com/v1/images:annotate"
+
+querystring = {"key": google_vision_api_key }
+headers = {'Content-Type': "application/json"}
+
+def encode_image(image_path):
+    with open(image_path, "rb") as image_file:
+        return base64.b64encode(image_file.read())
+
+def image_request(image_path):
+
+    payload = '{\"requests\":[{\"image\":{\"content\":\"'+
+    encode_image(image_path).decode('utf-8')+
+    '"},\"features\":[{\"type\":\"TEXT_DETECTION\"}]}]}'
+
+    response = requests.request("POST", url, data=payload, headers=headers, params=querystring)
+
+    return ast.literal_eval(response.text)
+```
+
+This is an example of the response:
+
+```{} 
+{'responses': [{'textAnnotations': [{'locale': 'ja',
+     'description': '-]\n一\n一本の傘を二人でさすこと。多く男女二人の場合に一あい-えん [哀婉](名) 哀れにやさしいこと。 こと。しん【愛郷心](名) 愛婚の精神。.............名)あいく\n-[製~Q)
+     れ]()あ\nの。0子持鮎の願漬。\nあいきょうp®(愛郷](名)生まれ故郷を愛する\nに\nVド\nし
+     いこと。叉、その程度。\n信的思想た打破すること。\n',
+     'boundingPoly': {'vertices': [{'x': 26, 'y': 21},
+       {'x': 1556, 'y': 21},
+       {'x': 1556, 'y': 2748},
+       {'x': 26, 'y': 2748}]}},
+    {'description': '-',
+     'boundingPoly': {'vertices': [{'x': 1227, 'y': 686},
+       {'x': 1227, 'y': 677},
+       {'x': 1262, 'y': 677},
+       {'x': 1262, 'y': 686}]}},
+
+       すること。\n'}}]}
+           {'description': '誘',
+     'boundingPoly': {'vertices': [{'x': 785, 'y': 880},
+       {'x': 814, 'y': 880},
+       {'x': 814, 'y': 914},
+       {'x': 785, 'y': 914}]}},
+    {'description': '(',
+     'boundingPoly': {'vertices': [{'x': 775, 'y': 916},
+       {'x': 814, 'y': 916},
+       {'x': 814, 'y': 940},
+       {'x': 775, 'y': 940}]}},
+    ...],
+```
+
+From the previous example, we can observe that the response returns a list of nested dictionaries.
+The first nested dictionary called **textAnnotations** consists of a list of nested dictionaries.
+Each one of those has a description (character) and boundingPoly (boundaries of the characters).
+
+### BoundingPoly
+
+Each boundingPoly consist of vertices in which the symbol is located.
+
+#### Region
+
+Te first object in the nested dictionary contains all identified characters in the image as well as the boundaries that comprises the location of those characters.
+This object can resemble the idea of the region provided in the Azure's API.
+
+Figure 8 shows the region identified by the API.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure8.png)
+ **Figure 8**
+
+#### The Character Boundaries
+
+The remaining objects enclose the boundaries of the characters. As it is shown in figure 9, each boundingPoly node can include one or more characters.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure9.png)
+**Figure 9**
+
+### Characters
+
+Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure 10. **Pending find a way to plot the text in vertical form to make it readable.**
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure10.png)
+**Figure 10**
+
+### languageHints
+
+Google Vision API offers the advantage of including in the request language hints.
+It consists of a list of languages the user knows in advance the image contains.
+For this study, we run two versions, one without hints and the other one with a list of two hints, such as Japanese and English, as the image contains some words in English.
+
+### Advantages and Disadvantages
+
+#### Advantages
+
+Same as the Azure API, this is also easy to use after reading the documentation.
+It also offers several examples in different programming languages using the Google libraries for Python.
+It gives the possibility to include languages in advanced as hints, and identifies the orientation automatically.
+The response contains an object with all identified characters in the correct order.
+
+Moreover, the API gives the opportunity to send the image in base64 format or using an internal (google storage) or external URL.
+
+#### Disadvantages
+
+Not clear at the moment.....I need to solve how to plot grouped characters vertically.
+
+### Future Work
+
+.........
 
@@
 
+# Appendix
+
 # References
@@
 5: https://docs.microsoft.com/en-us/azure/cognitive-services/computer-vision/quickstarts/python-print-text
+
+6: https://cloud.google.com/vision/docs/ocr

### 2020-09-06 outputs/documents/paper.Rmd
Add Pytesseract findings

@@
 
+Python-Tesseract is an optical character recognition (OCR) library for python.
+It is a wrapper for Google's Tesseract-OCR Engine.
+PyTesseract can read all image types such as png, jpeg, gif, tiff, BMP, among others.
+It is widely used to process everything from scanned documents.
+This inbuilt library of python performs the OCR techniques on the image to produce the digitized output text in a readable and editable form.
+
+To use this library, we need to install Tesseract. For this study, we use version 4. IT is necessary to call the .exe file to use Tesseract with PyTesseract. See the following example.
+
+```{python eval=FALSE, include=TRUE}
+#Call .exe location for Windows
+pytesseract.pytesseract.tesseract_cmd = r'C:\Program Files\Tesseract-OCR\tesseract.exe' 
+```
+
+Along with the PyTesseract library, the following libraries are used.
+
+```{python eval=FALSE, include=TRUE}
+from PIL import Image
+from PIL import ImageOps
+import pytesseract
+from os import path
+import pandas as pd
+import matplotlib.pyplot as plt
+from matplotlib.patches import Rectangle
+
+```
+
+PyTesseract offers several methods with different outputs when processing an image to extract text. According to Pypi.org, the uses of those methods are:
+
+- **image_to_string:** Returns the result of a Tesseract OCR run on the image to string
+- **image_to_boxes** Returns result containing recognized characters and their box boundaries
+- **image_to_data:** Returns result containing box boundaries, confidences, and other information. Requires Tesseract 3.05+. For more information, please check the Tesseract TSV documentation
+- **image_to_osd:** Returns result containing information about orientation and script detection.
+- **image_to_alto_xml:** Returns result in the form of Tesseract’s ALTO XML format.
+- **run_and_get_output:** Returns the raw output from Tesseract OCR. Gives a bit more control over the parameters that are sent to tesseract.
+
+For this analysis, we use the method image_to_data as this offers the boundaries and the recognized characters in a handy form so we can understand the process.
+Furthermore, in PyTesseract, it is needed to specify the language in advance.
+Since PyTesseract is a wrapper of Google's Tesseract-OCR Engine, Tesseract-OCR must have installed all required languages.
+In this case, it is Japanese, which is not included in its out-of-the-box version.
+To include a new language, adding the **.traineddata** file into the Tesseract-OCR/tessdata folder is sufficient.
+However, since the text in the image is vertical Japanese.
+It is necessary to include two files: jpn.traineddata and jpn_vert.traineddata.
+Once the files are located correctly, the following code extracts the text from the image.
+
+```{python eval=FALSE, include=TRUE}
+img1 = Image.open(r'~\inputs\00-sample-pages_1.png')
+image_to_data = pytesseract.image_to_data(img1, lang = 'jpn_vert')
+
+```
+
+The output from the previous code converted into a pandas dataframe is shown in figure 11.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure11.png)
+**Figure 11**
+
+From figure 11, we can observe that the output in the column **level** generates five levels.
+Those are pages, blocks, paragraphs, lines, and words (characters).
+Each one is subsets of the previous one.
+
+### Page
+
+For this example, the page resembles the concept of region, which is the largest area of the image enclosing all recognized characters. Figure 12 illustrates the page area.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure12.png)
+**Figure 12**
+
+### Blocks
+
+The blocks are subsets of the page area that consist of small groups of recognized characters.
+In figure 13, we can see that most of the blocks are well ordered.
+In terms of correctness of the boundaries, we can see that some of them overlap several characters that are not recognized by the library.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure13.png)
+**Figure 13**
+
+### Paragraphs
+
+Similar to the blocks, the paragraphs are subsets of blocks.
+These follow the same idea of subareas containing a set of characters.
+In this case, for example, we can look at paragraphs five and six, which are subsets of block five.
+It is interesting to see how the only paragraph (21) of block 12 is a smaller area compared to the block.
+This situation happens in several other blocks.
+See figure 14 for a better understanding.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure14.png)
+**Figure 14**
+
+### Lines
+
+Once the paragraphs are defined, the library provides in figure 15, the last subsets of characters called Lines.
+From the example, we can see that most of the characters are located in one of the lines.
+However, several others are not.
+Some of those cases are curious since there is no clear reason why those characters are not included.
+For instance, between the lines 65 and 66, two clear lines are not recognized by the library.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure15.png)   
+ **Figure 15**
+
+### Character Boundaries
+
+These boundaries enclose the characters.
+Figure 16 shows that a character boundary can include one or more characters.
+However, some character boundaries overlap with other ones.
+Moreover, the same as the previous areas, several characters have been skipped with no apparent reason.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure16.png)   
+ **Figure 16**
+
+### Characters
+
+In terms of character-level recognition, we can observe that many characters are not recognized.
+Interestingly those characters are in a correct block, paragraph, line, and character boundary, but it was skipped.
+For example, in the first line and the first character boundary of this line, there are two words, but one of them is not recognized.
+Figure 17 illustrates this case.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure17.png)   
+ **Figure 17**
+
+### Advantages and Disadvantages
+
+#### Advantages
+
+.......
+
+#### Disadvantages
+
+.....................
+
+### Future Work
+
 # Evaluation
@@
 6: https://cloud.google.com/vision/docs/ocr
+
+7: https://pypi.org/project/pytesseract/
+
+8: https://github.com/tesseract-ocr/tessdata
+
+9: https://github.com/UB-Mannheim/tesseract/wiki

### 2020-10-18 api-exploration/kraken-english/Kraken_Writeup.Rmd
add english exploration

---
title: "Kraken Exploration with English Text"
author: "Yian Wang"
date: "October 17, 2020"
output:
  pdf_document: default
header-includes:
  - \usepackage[document]{ragged2e}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, echo = TRUE, fig.align="center")

```

# 1. Introduction
Kraken is an easy-to-follow system used for Optical Character Recognition (OCR) [1]. The purpose of this exploration is to look at a one-page, one-column academic sample text to ensure kraken works sufficiently for English text before training it for Japanese characters.

# 2. Data
## 2.1 Sample Text
The sample "Reconciling with History: The Chinese-Canadian Head Tax Redress" by Peter Li [2] contains varying types of text - the title, author, main text, subheading, and footnote, and watermark are all different. Thus, an area of interest will be to see how kraken interprets the different types of text, in particular, the 1 superscript in the subheading "Origin of the Chinese Head Tax in Canada". \
Keeping the green highlighted areas in the document tests the effectiveness of binarization in kraken.\
As per the tutorial, the sample is imported as a tif filetype.

```{r echo=FALSE, eval = TRUE, out.width='50%'}
knitr::include_graphics('/Users/yianwang/Desktop/kraken/inputpic.png')
```
\center __Figure 1.__ Sample Input Text: Reconciling with History

\justify
## 2.2 en_best.mlmodel
In the current kraken version to date, this model was not included but was required to run the code. It must be downloaded and imported separately (**[click here to download](https://github.com/mittagessen/kraken/issues/120)** - see mittagessen's comment on Feb 15, 2019).

# 3. Kraken Exploration

## 3.1 Local
The kraken tutorial is easily followed locally; however, for this process to be as accessible and reproducible as possible, this exploration focuses on getting the process to work on some cloud platform such as Jupyter Hub or Google Colab.

## 3.2 Jupyter Notebook/Jupyter Hub
JupyterLab on Jupyter Hub is a free cloud platform to share code.

### 3.2.1 Error
Attempting to use kraken in the JupyterLab terminal, the shell runs out of memory before the package fully installs.\ The first command 
```{bash}
pip install kraken
```
reaches a certain point in memory usage (1.84/2.00 GB) and proceeds to quit (See Appendix Figure A). The conclusion is that Jupyter Hub does not have adequate memory space so other platforms need to be explored.

## 3.3 Google Colab
Google Golab was chosen next as it has more space than JupyterHub.

### 3.3.1 Pricing
While Google Colab is free for up to 12GB of memory and run time of 12 hours, paying $9.99 a month gives access to 25GB and up to 24 hours of run time [3]. Though the free version is sufficient for the scope of this exploration task, this removes any fear of running out of space on this platform for the time being.\ Nonetheless, the discussion of pricing is important in order to gauge whether it's worth it to use the platform if/when there is a high volume of data.

### 3.3.2 Method and Outputs

First install kraken:
```{bash}
pip install kraken
```

Before beginning the process, upload the tif file of the desired text, as well as the ```en_best.mlmodel``` file to the Colab environment. \

Now, binarize the image to remove any color to allow kraken to analyze it:
```{bash}
!kraken -i image.tif bw.png binarize
```

Then, take the binarized image output and turn it into a txt file:
```{bash}
!kraken -i bw.png image.txt binarize segment ocr -m en_best.mlmodel
```
\
\newpage
Alternatively, it is possible to binarize and convert to a txt file in one line:
```{bash}
!kraken -i image.tif onestep_image.txt binarize segment ocr -m en_best.mlmodel
```

The resulting txt file is promising, with minimal errors, mostly in the title (See Appendix Figure B). \
To analyse the issue, check the line boundaries to see if kraken detected the title area (and other areas of error) correctly. A json file of the boundaries is obtained and plotted around the text to see if there exist any unexpected boundaries.\
\
Get the json file as follows: 
```{bash}
!kraken -i bw.png lines.json segment
```

Then run a function ```show_boxes``` (see Appendix 6.1) to plot these boundaries. The output is as follows:

```{r echo=FALSE, eval = TRUE, out.width='50%'}
knitr::include_graphics('/Users/yianwang/Desktop/kraken/boundaries.png')
```
\center__Figure 2.__ Sample Text with Line Boundaries

\justify
It can be see that kraken evaluated the boundaries well in this sample, with exception to the title, which has many strange boundary boxes around it. This explains the discrepancy in the produced txt file.

# 4. Evaluation

Kraken was fairly easy-to-use, and the online tutorial was very intuitive. It identified the words in the sample correctly with only minor errors. \
However, the boundaries were found at a line level, rather than a word or character level, which is less effective and sensitive. Additionally, the ```en_best.mlmodel``` file was not installed with kraken in the command line, though that issue was easily solved.

# 5. Sources
1. kraken — kraken 2.0.5-4-gbb42ba5  documentation [Internet]. Kraken.re. 2015 [cited 2020 Oct 18]. Available from: http://kraken.re/index.html \

2. Li P. Reconciling with History: The Chinese-Canadian Head Tax Redress. Journal of Chinese Overseas [Internet]. 2008 [cited 2020 Oct 18];4(1):127–40. Available from: https://brill.com/view/journals/jco/4/1/article-p127_9.xml DOI: 10.1163/179325408788691507 \

3. Google newly launches Colab Pro! - comparison of Colab and Colab pro · Buomsoo Kim [Internet]. Github.io. 2020 [cited 2020 Oct 18]. Available from: https://buomsoo-kim.github.io/colab/2020/03/15/Google-newly-launches-colab-pro.md/

# 6. Appendix
## 6.1 Code

```{python python.reticulate = FALSE}
def show_boxes(img2):
  """ 
  Find line boundaries on image text
  """
  from PIL import ImageDraw, Image
  with Image.open(img2) as img:
    drawing_object = ImageDraw.Draw(img)
    bounding_boxes = pageseg.segment(img.convert('1'), text_direction = 'horizontal-lr', 
      black_colseps = False)['boxes']
    for box in bounding_boxes:
      drawing_object.rectangle(box, fill = None, outline = 'red')
    return img
```

## 6.2 Images
```{r echo=FALSE, eval = TRUE, out.width='50%'}
knitr::include_graphics('/Users/yianwang/Desktop/kraken/memoryquit.png')
```
\center __Figure A.__ Memory in Jupyter Hub Terminal
\
\

```{r echo=FALSE, eval = TRUE, out.width='40%'}
knitr::include_graphics('/Users/yianwang/Desktop/kraken/txtfiless.png')
```
\center __Figure B.__ txt File Output

### 2020-10-26 outputs/documents/paper.Rmd
Clarification about Amazon Textract and Kraken and Amazon notebooks
Include Kraken findings and training data

@@
 
+## Kraken - Python Library
+
+Kraken is a python library created by Benjamin Kiessling from Université PSL in France and Leipzig University.
+This library is a combination of a fork (independent development built on an existing one) from the Ocropus package and CLSTM neural network library.
+Its purpose was to improve accuracy and performance rates compared with Ocropus.
+It has been tested with languages such as Arabic, Persian, Syriac Polytonic Greek, Latin, among other.
+However, there is no information about japanese-trained models.
+
+To assess the performance of this library, it is necessary to train a model for japanese texts.
+To do that, Kraken offers a  function called **train**.
+This function expects a series of images that according to Kraken´s website, these images must be high quality scans, preferably color or grayscale, and at least 300dpi.
+Images in PDF format are not allowed.
+Each image must be accompanied with a text file with extension .gt.txt.
+This file will contain the character(s) that corresponds to the image with the same name.
+For instance in figure xx we see the image file is called **sec1_line1.png**, the pair-wise text element for this image is **sec_line.gt.txt**.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure18.png)   
+ **Figure 18**
+
+After the training stage, Kraken analyses the layout and extracts text lines from an input image for later processing by the recognition.
+A step by step process is provided by Kraken´s website (http://kraken.re/index.html) to recognize text from an image using the model we want.
+
+### Training process challenges
+
+The training process itself is very friendly.
+However, the data preparation is the most important part as it generates the samples we feed into the model.
+Other studies pointed out that for languages such as Arabic, at least 800 lines are required to train a descent model.
+For the japanese text of this study we trained 36 lines in which several characters appear more than once.
+
+## Amazon Textract
+
+According to Amazon's website, Amazon Textract can detect Latin-script characters from the standard English alphabet and ASCII symbols.
+
+https://aws.amazon.com/textract/faqs/
+
+## Amazon Rekognition
+
+According to Amazon's website, Amazon Rekognition supports text in most Latin scripts and numbers.
+Text detection recognizes up to 50 sequences of characters per the image or video frame and lists them as words and lines.
+
+https://aws.amazon.com/rekognition/faqs/
+
 # Evaluation

### 2020-11-29 outputs/documents/paper.Rmd
Update Google, Azure, and Pytesseract to the Sections approach.

@@
 In that case, there is no barrier in the process of extracting data.
-But other times it is not as easy if it is an image, a survey form, or complex shapes containing relevant information, .
+But other times it is not as easy if it is an image, a survey form, or complex shapes containing relevant information.
 Furthermore, there is a linguistic component that adds more complexity.
@@
 
+For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the tools.
+This image contains 3293 characters.
+Words in English were counted as one character for this analysis.
+MOreover, the sample text was divided into four images as it is illustrated in figure XX.
+These new images were assessed across all tools.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/sections.png)
+**Figure XX**
+
 ## OCR options
@@
 | Amazon Rekognition	                 | Amazon	   | API		        | First 1 million images: $0.001 per image <br/> <br/> Next 9 million images $0.0008 per image <br/> <br/> Next 90 million images $0.0006 per image <br/> <br/> Over 100 million images $0.0004 per image         |                    |
-| Tesseract		                         |           | R library      | Free	  |                    |
 | PyTesseract (Wrapper Google's OCR Engine)    |           | Python Library | Free    |                    |
-| OpenCV		                           |           | Python Library | Free	  |                    |
-| Watson Visual Recognition	           | IBM	     | API		        | Lite: 1000/Free, <br/> <br/> Standard: $0.002 per trans      |                    |
+Standard: $0.002 per trans      |                    |
 | Kraken	(Linux OS)                   |           | Python Library	| Free	  |                    |
 | Google Vision (for Text recognition) | Google	   | API		        | 1000/Free, 5 mill/$1.5, >5mill/$0.6        |                    |
-| SwiftOCR	(iOS)                      | Apple	   | Swift Library  |         |                    | 		
 | Amazon Textract	                     | Amazon	   | API		        | First 1 Million pages: $0.015 - $0.05 per page, <br/> <br/> Over 1 Million pages: $0.01 - $0.04 per page        |                    |
-|	Tensorflow                           | Google    | Python Library | Free    |                    |
+|	Kindai-OCR                           | Google    | Python Library | Free    |                    |
 
@@
 
-Figure 1 presents a sample that corresponds to a Japanese text, but it also contains English text in some fragments of the text.
+Figure 1 presents a sample that corresponds to the section1 of the image containing Japanese text, but it also contains English text in some fragments of the text.
 The API offers the possibility to do self-detection, which in this case is helpful, but also the opportunity to specify the language in advance.
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure1_full.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/section1.png)
 **Figure 1**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure2_full.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/region-section1.png)
  **Figure 2**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure3_full.png)   
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/lines-section1.png)   
  **Figure 3**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure4_full.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/boundaries-section1.png)
  **Figure 4**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure5_full.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/characters-section1.png)
  **Figure 5**
@@
 This situation makes it difficult for researchers to organize the information correctly as the order of the characters matter.
-
-### Future Analysis
-
-By doing some image preprocessing before the API call, it might be possible to see improvements in terms of boundary identification....
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure8.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/sections.png)
  **Figure 8**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure9.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/boundaries.png)
 **Figure 9**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure10.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/characters.png)
+
 **Figure 10**
@@
 #### Disadvantages
-
-Not clear at the moment.....I need to solve how to plot grouped characters vertically.
-
-### Future Work
-
-.........
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure12.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/page.png)
 **Figure 12**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure13.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/blocks.png)
 **Figure 13**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure14.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/paragraphs.png)
 **Figure 14**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure15.png)   
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/lines.png)   
  **Figure 15**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure16.png)   
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/boundaries.png)   
  **Figure 16**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure17.png)   
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/characters.png)   
  **Figure 17**
@@
 
-.......
+The most important advantage is that this is a free library.
+It is also a wrapper from Google's Tesseract Engine.
+Moreover, the way it presents the covered areas are very detailed.
+It offers blocks, paragraphs, lines, boundaries, and finally the character level.
 
 #### Disadvantages
-
-.....................
-
-### Future Work
 
@@
 Other studies pointed out that for languages such as Arabic, at least 800 lines are required to train a descent model.
-For the japanese text of this study we trained 36 lines in which several characters appear more than once.
+For the Japanese text of this study we trained 36 lines in which several characters appear more than once.
+The result after the training process was not good, indicating that the need of greater sample data might be needed which is not in the scope of this study.
+
+# Other limitations
+
+In order to use this library it is required to have either Linux or Mac. In this study, we use Google Colab which is offers a Linux environment to assess the library.
 

### 2020-12-01 outputs/documents/paper.Rmd
doc update and section three kindai

@@
 | Amazon Textract	                     | Amazon	   | API		        | First 1 Million pages: $0.015 - $0.05 per page, <br/> <br/> Over 1 Million pages: $0.01 - $0.04 per page        |                    |
-|	Kindai-OCR                           | Google    | Python Library | Free    |                    |
+|	Kindai-OCR                           | Result of n2i Project    | Python Library | Free    |                    |
 
@@
 
+## Kindai-OCR
+
 ## Kraken - Python Library
@@
 
+In terms of flexibility...
+
+Sequence of the characters...
+
+Output given...xml, json, flat file, csv...
+
+NUmber of characters well recognized...(Accuracy)
+
 The main aspect of the end product will be a graph with two axis, and dots for where each service is positioned, coloured or faceted by the test.

### 2020-12-02 outputs/documents/paper.Rmd
Text Update. Change some image references to github url

@@
 
-Japanese dictionaries...
+Japanese dictionaries...[Rohan]
 
-For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the tools.
+For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the selected OCR tools.
 This image contains 3293 characters.
 Words in English were counted as one character for this analysis.
-MOreover, the sample text was divided into four images as it is illustrated in figure XX.
-These new images were assessed across all tools.
+MOreover, the sample text was divided into four images called **sections** as it is illustrated in figure XX.
+These new images were assessed across all OCR tools.
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/sections.png)
+![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/outputs/documents/sections.png)
 **Figure XX**
+
+This example is in a vertical form, meaning that it should be read it from right to left and from the top to the bottom.
+This is important since it is expected to obtain from each OCR tool the correct sequence of characters.
+FOr instance, from section 1 in figure xx, the first five characters from the first line are **[一本の傘を]**
+
+The following figures corresponds to each section extracted from the sample:
+
+![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_1.png)
+**Figure XX Section 1**
+
+![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_2.png)
+**Figure XX Section 2**
+
+![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_3.png)
+**Figure XX Section 3**
+
+![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_4.png)
+**Figure XX Section 4**
 
@@
 
-The following list contains some of the OCR APIs and libraries available that will be evaluated in this study:
+The following list contains the OCR APIs and libraries available that will be evaluated in this study:
 
@@
 
-Figure 1 presents a sample that corresponds to the section1 of the image containing Japanese text, but it also contains English text in some fragments of the text.
+Figure 1 presents a sample that corresponds to the section 1 of the image containing Japanese text, but it also contains English text in some fragments of the text.
 The API offers the possibility to do self-detection, which in this case is helpful, but also the opportunity to specify the language in advance.
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure6_full.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/self-detection.png)
  **Figure 6**
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure7_full.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/japanese-parameter.png)
  **Figure 7**
-
-In general, self-detection and the case with the language parameter as the Japanese do not generate the boundaries correctly.
-In Figures 6 and 7, we can observe that both cross the line, which is not correct for in this document.
-There is a line delimiting the boundaries of the text, but it has been ignored by both API calls.
-This situation makes it difficult for researchers to organize the information correctly as the order of the characters matter.
 
@@
 
+Some lines were completely ignored by Pyteseract, even thought it was clear enough to be recognized by the tool.
+
 ## Kindai-OCR

### 2020-12-02 outputs/documents/paper.Rmd
Add Kindai to the document.

@@
 
+According to the Center for Open Data in the Humanities, Kindai-OCR is an OCR system for modern Japanese documents.
+It was built under the N2I project that study state-of-the-art statistical models for OCR, and work on the development of infrastructure and providing open access to data.
+The datasets were constructed by the University of Tokyo Center for Education and Research and the National Institute of Japanese Language and are used for OCR machine learning.
+These datasets are commonly known as the Modern Magazine Datasets.
+
+The Kindai-OCR code was developed in Python and released as an open source code in August 2020 on Github..The Github folder contains all the necessary code and instructions to assess the OCR tool.
+**[not sure if it is necessary to mention the modification in the file test.py, in order to run the model using GPUs.]**
+
+After running the Kindai-OCR for our samples, the system generated two main outputs. They are explained as follows:
+
+### File result.xml
+
+This file is presented in an Extensible Markup Language (XML) format containing a tree with the identified lines, as well as the corresponding characters. An example of the is shown as follows:
+
+```{}
+<?xml version='1.0' encoding='Shift_JIS'?>
+<paper xmlns="http://codh.rois.ac.jp/modern-magazine/"><page dpi="100" file="00-sample_pages_3_sec_3.png" height="1040" number="1" width="2430"><line height="905" width="72" x="332" y="0">あいくるし發路事、愛くるし（形、</line><line height="1026" width="76" x="466" y="0">あいくち島（合巳。名。あれせも。ものよ</line><line height="1026" width="69" x="592" y="0">あいくすりし（（きき」名その人の爲に信身あ</line><line height="1031" width="65" x="660" y="0">あいきん（及兵」（名起しい得をうつし表しした</line><line height="1031" width="78" x="778" y="0">あいきん愛心。名客する東なふする、</line><line height="361" width="72" x="849" y="0">あいきよう對</line><line height="292" width="64" x="918" y="0">あいきよう</line><line height="1031" width="64" x="981" y="0">あいきよう對（愛婦（名（（（らきささ。（（彼。。</line><line height="292" width="64" x="2264" y="0">あいきまう</line><line height="997" width="69" x="1749" y="34">（愛教商）名」名毎金。造。。愛もがなてては立</line><line height="337" width="55" x="286" y="38">府がはゆらしい。</line><line height="930" width="68" x="407" y="38">くあふ人。○つばのない兌。。ヒ直。九五五五。</line>
+```
+
+After transforming this file into a dataframe form, we found that 238 lines with their corresponding characters, were generated.
+In figure XX we can see that the result.xml file provides information such as the corresponding level (paper, page, or line) in the tag column, the identified characters in the text column, the associated image the file column, among other attributes.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/kindai-images/xml-processed.png)   
+ **Figure XX**
+
+### New version of the image
+
+Kindai-OCR generated a new version of the image containing the identified lines and characters. An example is shown as follows in figure xx.
+
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/kindai-images/kindai-section1.jpg)
+**Figure XX**
+
+### Advantages and Disadvantages
+
+#### Advantages
+
+Same as libraries such as Pytesseract, one of The most important advantages is that it is a free tool.
+Moreover, the recognition process is very easy.
+To obtain results just by putting the images in the test folder and running the file called test.py on Python is enough to obtain the results.
+
+#### Disadvantages
+
+At the time of this assessment, the use of GPUs is required which is a limitation to take into account. For this study, we used Colab from Google, which offers this capability.
+
 ## Kraken - Python Library
@@
 9: https://github.com/UB-Mannheim/tesseract/wiki
+
+10: http://codh.rois.ac.jp/software/kindai-ocr/
+
+11: https://github.com/ducanh841988/Kindai-OCR
+
+12: Anh Duc Le, Daichi Mochihashi, Katsuya Masuda, Hideki Mima, and Nam Tuan Ly.
+2019.
+Recognition of Japanese historical text lines by an attention-based encoder-decoder and text line generation.
+In Proceedings of the 5th International Workshop on Historical Document Imaging and Processing (HIP ’19).
+Association for Computing Machinery, New York, NY, USA, 37–41.
+DOI:https://doi.org/10.1145/3352631.3352641

### 2020-12-02 outputs/documents/paper.tex
Add Kindai to the document.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Notes and approaches to OCR},
  pdfauthor={Rohan Alexander, John Tang, Diego Mamanche Castellanos},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\title{Notes and approaches to OCR}
\author{Rohan Alexander, John Tang, Diego Mamanche Castellanos}
\date{08 August 2020}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

A crucial aspect of the data science workflow is gathering data. It
involves the tools and methods used to collect information in an
established systematic fashion and identify the variables being
measured. It also describes the methods used to obtain the data.
Although the data collection component of research remains the same
regardless of the field of study, the methods used vary among those
fields of study as they have different interests. Moreover, the
diversity of data types adds complexity to the process of gathering
data. Structured data is organized in a highly regular manner or a
pre-defined data model where the regularities apply to all the data in a
particular dataset. Some examples are tables and relations.
Semi-structured data contains this same information, but instead of
having regular structures applied to all items in the dataset, the data
might be interpreted with structural information. It can be supplied as
tags e.g.~name = ``Bob'' but also other markers to separate semantic
elements and enforce hierarchies of records and fields within the data.
Finally, Unstructured data, such as texts or images, holds information
with no explicit structured data, such as tags. However, these tags may
be assigned using manual or automatic techniques, converting the
unstructured data to semi-structured data \((Robert M. Losee, 2005)^1\).
This diversity and complexity of data structures complicate, even more,
the data gathering process as each data type may require a specific
gathering approach(es) when needed.

The Portable Document Format (PDF) is an example of unstructured data
created by the company Adobe in the 90s. It is widely used for
documents. According to the \(ISO 32000-2:2017^2\), the latest edition
of the PDF Reference (2.0), PDF enables users to exchange and view
electronic documents easily and reliably, independent of the environment
in which they were created or the environment in which they are viewed
or printed. It is intended to fulfill the following requirements:

\begin{itemize}
\tightlist
\item
  preservation of document fidelity independent of the device, platform,
  and software,
\item
  merging of content from diverse sources --- Web sites, word processing
  and spreadsheet programs, scanned documents, photos, and graphics ---
  into one self-contained document while maintaining the integrity of
  all original source documents,
\item
  an extensible metadata model at the document and object level,
\item
  collaborative editing of documents from multiple locations or
  platforms,
\item
  digital signatures to certify authenticity,
\item
  security and permissions to allow the creator to retain control of the
  document and associated rights,
\item
  accessibility of content to those with disabilities,
\item
  extraction and reuse of content for use with other file formats and
  applications, and
\item
  electronic forms to gather and/or represent data within business
  systems.
\end{itemize}

To mention some of the features incorporated in this version we have:

\begin{itemize}
\tightlist
\item
  12.10, ``Geospatial features'';
\item
  13.7, ``Rich media'' annotations;
\item
  14.7.4, ``Namespaces'' for tagged PDF;
\item
  14.9.6, ``Pronunciation hints'';
\item
  14.12, ``Document parts'';
\item
  14.13, ``Associated files'';
\item
  Support for PRC (see 13.6, ``3D Artwork'');
\item
  Support for UTF-8.
\end{itemize}

However, these advantages mean that the data in PDFs cannot be used for
quantitative statistical analysis. The reason is that it needs
measurable and verifiable data. But PDF documents, as it was mentioned
previously, can have different objects, some of them non-static objects
compressed in the same document. This situation makes it difficult to
extract valuable information from the paper.

Sometimes just by copying and pasting the information directly from the
PDF is possible when it contains simple texts or regular tables. In that
case, there is no barrier in the process of extracting data. But other
times it is not as easy if it is an image, a survey form, or complex
shapes containing relevant information. Furthermore, there is a
linguistic component that adds more complexity. For instance, it is well
known that non-Latin characters such as Japanese, Chinese, Arabic, among
others, generate several difficulties in different stages of the text
mining process. It is because those characters have complicated
structures, a huge number of categories, and resemblance among
characters, font unevenness, or writing styles. In those cases, the need
for reliable tools or methods with the ability to elicit data becomes
extremely important.

Optical character recognition (OCR), a process that transforms a
bitmapped image of printed or handwritten text into text code, and
thereby making it machine-readable, has been widely used for scientists
trying to capture the images of characters and texts back in the 50s.
First, by mechanical and optical means of rotating disks and
photomultiplier flying spot scanner with a cathode ray tube lens,
followed by photocells and arrays of them. The OCR process was slow, and
one line of characters could be digitized at a time. Nowadays, in OCR,
once a printed or handwritten text has been captured optically by a
scanner or some other optical means, the digital image goes through the
following stages of a computer recognition system
\((Cheriet, Mohamed; Kharma, 2007)^3\):

\begin{itemize}
\tightlist
\item
  The preprocessing stage that enhances the quality of the input image
  and locates the data of interest.
\item
  The feature extraction stage that captures the distinctive
  characteristics of the digitized characters for recognition.
\item
  The classification stage that processes the feature vectors to
  identify the characters and words.
\end{itemize}

In this paper we review various OCR options for researchers who need to
gather data from PDFs in which the text must be extracted to be reused,
edited, or reformatted; the text should be available for full-text
information retrieval; the text is to be coded in HTML or SGML; the text
should be available to adaptive equipment for the visually impaired; the
file size is of concern (in terms of storage or bandwidth to transmit);
or the resources are available to perform OCR and correct the output.

\textbf{When they consider a primer on what OCR options exist these days
depending on your technical ability and then how they perform for an
easy example and then how they perform for a hard example (the Japanese
extract) and finally some suggestions for what is needed in the
future\ldots.}

\textbf{Our paper represents\ldots{}}

\textbf{The remainder of this paper is structured as follows\ldots{}}

\hypertarget{data}{%
\section{Data}\label{data}}

\hypertarget{test-samples}{%
\subsection{Test Samples}\label{test-samples}}

Japanese dictionaries\ldots{[}Rohan{]}

For the purpose of this study, one page from the letter a in the
Japanese dictionary was taken to assess the selected OCR tools. This
image contains 3293 characters. Words in English were counted as one
character for this analysis. MOreover, the sample text was divided into
four images called \textbf{sections} as it is illustrated in figure XX.
These new images were assessed across all OCR tools.

\includegraphics{https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/outputs/documents/sections.png}
\textbf{Figure XX}

This example is in a vertical form, meaning that it should be read it
from right to left and from the top to the bottom. This is important
since it is expected to obtain from each OCR tool the correct sequence
of characters. FOr instance, from section 1 in figure xx, the first five
characters from the first line are \textbf{{[}一本の傘を{]}}

The following figures corresponds to each section extracted from the
sample:

\includegraphics{https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped\%20pages/00-sample_pages_3_sec_1.png}
\textbf{Figure XX Section 1}

\includegraphics{https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped\%20pages/00-sample_pages_3_sec_2.png}
\textbf{Figure XX Section 2}

\includegraphics{https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped\%20pages/00-sample_pages_3_sec_3.png}
\textbf{Figure XX Section 3}

\includegraphics{https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped\%20pages/00-sample_pages_3_sec_4.png}
\textbf{Figure XX Section 4}

\hypertarget{ocr-options}{%
\subsection{OCR options}\label{ocr-options}}

The following list contains the OCR APIs and libraries available that
will be evaluated in this study:

\begin{longtable}[]{@{}lllll@{}}
\toprule
\begin{minipage}[b]{0.37\columnwidth}\raggedright
OCR Tool\strut
\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright
Company\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
Type\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedright
Monthly Price Aug/2020\strut
\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
Tech Requierements\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.37\columnwidth}\raggedright
Azure Cognitive Services (OCR)\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
Microsoft\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
API\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
Free Web Container: 5000/Free; S1 Web Container: 0-1M/\$1.50 per 1,000
trans, 1M-5M/\$1 per 1,000 trans, 5M-10M/\$0.65 per 1,000 trans,
10M-100M/\$0.65 per 1,000 trans, +100M/\$0.65 per 1,000 trans\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.37\columnwidth}\raggedright
Amazon Rekognition\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
Amazon\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
API\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
First 1 million images: \$0.001 per image Next 9 million images \$0.0008
per image Next 90 million images \$0.0006 per image Over 100 million
images \$0.0004 per image\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.37\columnwidth}\raggedright
PyTesseract (Wrapper Google's OCR Engine)\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
Python Library\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
Free\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.37\columnwidth}\raggedright
Standard: \$0.002 per trans\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.37\columnwidth}\raggedright
Kraken (Linux OS)\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
Python Library\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
Free\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.37\columnwidth}\raggedright
Google Vision (for Text recognition)\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
Google\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
API\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
1000/Free, 5 mill/\$1.5, \textgreater5mill/\$0.6\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.37\columnwidth}\raggedright
Amazon Textract\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
Amazon\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
API\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
First 1 Million pages: \$0.015 - \$0.05 per page, Over 1 Million pages:
\$0.01 - \$0.04 per page\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.37\columnwidth}\raggedright
Kindai-OCR\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
Result of n2i Project\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
Python Library\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright
Free\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{azure-corgnitive-services---computer-vision-ocr}{%
\subsection{Azure Corgnitive Services - Computer Vision
OCR}\label{azure-corgnitive-services---computer-vision-ocr}}

Among the Microsoft Azure's portfolio, Azure Cognitive Services offers
Computer Vision, an API that processes images and returns information
based on the visual features the user is interested in. Those services
comprise object detection of an image, visual features tagging, image
categorization, Optical Character Recognition (OCR), among \(others^4\).
The OCR API processes an image and returns the language of the document,
orientation, regions, lines, and finally, the characters.

In python we need several libraries for calling the API.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ os}
\ImportTok{import}\NormalTok{ sys}
\ImportTok{import}\NormalTok{ requests}
\CommentTok{# If you are using a Jupyter notebook, uncomment the following line.}
\CommentTok{#%matplotlib inline}
\ImportTok{import}\NormalTok{ matplotlib.pyplot }\ImportTok{as}\NormalTok{ plt}
\ImportTok{from}\NormalTok{ matplotlib.patches }\ImportTok{import}\NormalTok{ Rectangle}
\ImportTok{from}\NormalTok{ PIL }\ImportTok{import}\NormalTok{ Image}
\ImportTok{from}\NormalTok{ io }\ImportTok{import}\NormalTok{ BytesIO}
\ImportTok{import}\NormalTok{ matplotlib}
\ImportTok{from}\NormalTok{ os }\ImportTok{import}\NormalTok{ path}
\ImportTok{import}\NormalTok{ ast}
\end{Highlighting}
\end{Shaded}

Then, we need to create headers and parameters necessary for calling the
API. The library \textbf{requests} is commonly used in python to do
that. The method \textbf{post} is needed as the API uses the HTTP method
POST.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Create the URL for the API call. The endpoint corresponds to the Azure's }
\CommentTok{# endpoint of the account.}
\NormalTok{ocr_url }\OperatorTok{=}\NormalTok{ endpoint }\OperatorTok{+} \StringTok{"vision/v3.0/ocr"}

\CommentTok{#Create the header using the Azure's subscription key.}
\NormalTok{headers }\OperatorTok{=}\NormalTok{ \{}\StringTok{'Ocp-Apim-Subscription-Key'}\NormalTok{: subscription_key\} }

\CommentTok{#In params language': 'ja' for japanese only. 'unk' means self detection }
\NormalTok{params }\OperatorTok{=}\NormalTok{ \{}\StringTok{'language'}\NormalTok{: }\StringTok{'unk'}\NormalTok{, }\StringTok{'detectOrientation'}\NormalTok{: }\StringTok{'true'}\NormalTok{\} }
\NormalTok{data }\OperatorTok{=}\NormalTok{ \{}\StringTok{'url'}\NormalTok{: image_url\}}

\CommentTok{#Call and save the response using the method post from the library request}
\NormalTok{response }\OperatorTok{=}\NormalTok{ requests.post(ocr_url, headers}\OperatorTok{=}\NormalTok{headers, params}\OperatorTok{=}\NormalTok{params, json}\OperatorTok{=}\NormalTok{data)}
\end{Highlighting}
\end{Shaded}

Here we have an example of the response:

\begin{verbatim}
{'language': 'ja',
 'textAngle': 0.0,
 'orientation': 'Up',
 'regions': [{'boundingBox': '31,30,1521,2721',
   'lines': [{'boundingBox': '730,30,44,2718',
     'words': [{'boundingBox': '735,30,34,34', 'text': 'あ'},
      {'boundingBox': '736,71,34,26', 'text': 'い'},
      {'boundingBox': '749,100,6,11', 'text': '・'},
      {'boundingBox': '735,116,34,27', 'text': 'い'},
      {'boundingBox': '736,149,33,33', 'text': 'ん'},
\end{verbatim}

\hypertarget{language-and-orientation}{%
\subsubsection{Language and
Orientation}\label{language-and-orientation}}

Figure 1 presents a sample that corresponds to the section 1 of the
image containing Japanese text, but it also contains English text in
some fragments of the text. The API offers the possibility to do
self-detection, which in this case is helpful, but also the opportunity
to specify the language in advance. Moreover, the orientation can also
be self-detected or not.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/section1.png}
\textbf{Figure 1}

\hypertarget{regions}{%
\subsubsection{Regions}\label{regions}}

The blue line figure 2 denotes the segment from the image that includes
the characters. In this example, there is only one blue line because the
document is only text. In other cases, it may contain images requiring
more than one region.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/region-section1.png}
\textbf{Figure 2}

\hypertarget{lines}{%
\subsubsection{Lines}\label{lines}}

Once the region is defined, the API provides in figure 3 (red
rectangles) the subsets of characters of the region called Lines. From
the example, we can see that some characters are not included in any of
the lines. Those characters are not recognized by the API.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/lines-section1.png}\\
\textbf{Figure 3}

\hypertarget{the-character-boundaries}{%
\subsubsection{The Character
Boundaries}\label{the-character-boundaries}}

After the lines are identified, the API provides in figure 4 each
recognized character bounding boxes. Those without a yellow square were
not recognized by the API in this example.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/boundaries-section1.png}
\textbf{Figure 4}

\hypertarget{characters}{%
\subsubsection{Characters}\label{characters}}

Once the bounding boxes are located, each character takes its
corresponding place, as it is shown in figure 5.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/characters-section1.png}
\textbf{Figure 5}

\hypertarget{advantages-and-disadvantages}{%
\subsubsection{Advantages and
Disadvantages}\label{advantages-and-disadvantages}}

\hypertarget{advantages}{%
\paragraph{Advantages}\label{advantages}}

The API is easy to use after reading the documentation. It offers an
example of how to use it in different programming languages. It also
offers the possibility to self-detect languages and the orientation of
the document. The response is clear, and extract the information from
the JSON file is not complicated.

\hypertarget{disadvantages}{%
\paragraph{Disadvantages}\label{disadvantages}}

Even though the API offers the possibility to self-detect the language,
It changes the order in which the characters should be in the output. In
figures 6 we can see that the first line provided by the self-detection
approach is located in the middle. This situation does not allow a
correct interpretation of the text because it does not follow the
reading pattern. In this case, it is a vertical orientation, which means
we have to read it from right to left.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/self-detection.png}
\textbf{Figure 6}

When the parameter language is stated as Japanese since the beginning,
as we can see in figure 7, it recognizes the first line correctly.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/japanese-parameter.png}
\textbf{Figure 7}

\hypertarget{google-vision-ocr}{%
\subsection{Google Vision OCR}\label{google-vision-ocr}}

Google Vision API can integrate vision detection features, including
image labeling, face and landmark detection, optical character
recognition (OCR), and tagging of explicit content. The text recognition
process detects text in images and recognizes the text contained
therein. Once detected, the recognizer then determines the actual text
in each block and segments it into lines and words.

To evaluate this OCR option, we need the following python libraries.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ os }\ImportTok{import}\NormalTok{ path}
\ImportTok{from}\NormalTok{ PIL }\ImportTok{import}\NormalTok{ Image}
\ImportTok{from}\NormalTok{ PIL }\ImportTok{import}\NormalTok{ ImageFont}
\ImportTok{from}\NormalTok{ PIL }\ImportTok{import}\NormalTok{ ImageDraw}
\ImportTok{from}\NormalTok{ PIL }\ImportTok{import}\NormalTok{ ImageEnhance}
\ImportTok{import}\NormalTok{ base64 }\CommentTok{#Convert an image into base64 form for API requests}
\ImportTok{import}\NormalTok{ requests }\CommentTok{#API request - GET/POST}
\ImportTok{import}\NormalTok{ json}
\ImportTok{import}\NormalTok{ ast}
\end{Highlighting}
\end{Shaded}

Same as the Azure API, we need to create the headers and parameters
necessary for calling the API. We also need the python library
\textbf{requests} to make the API call. The method \textbf{post} is
needed as the API uses the HTTP method POST.

The following example illustrates how to state the headers and
parameter, but also create two functions. The first one, called
encode\_image converts an image into base64, an encoding process
designed to carry data stored in binary formats across channels that
only reliably support text content. It can embed image files or other
binary assets inside textual assets. The second one makes an HTTP POST
request that calls Google's Vision API.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Create the URL for the API call. The endpoint corresponds to the Azure's }
\CommentTok{# endpoint of the account.}
\NormalTok{url }\OperatorTok{=} \StringTok{"https://vision.googleapis.com/v1/images:annotate"}

\NormalTok{querystring }\OperatorTok{=}\NormalTok{ \{}\StringTok{"key"}\NormalTok{: google_vision_api_key \}}
\NormalTok{headers }\OperatorTok{=}\NormalTok{ \{}\StringTok{'Content-Type'}\NormalTok{: }\StringTok{"application/json"}\NormalTok{\}}

\KeywordTok{def}\NormalTok{ encode_image(image_path):}
    \ControlFlowTok{with} \BuiltInTok{open}\NormalTok{(image_path, }\StringTok{"rb"}\NormalTok{) }\ImportTok{as}\NormalTok{ image_file:}
        \ControlFlowTok{return}\NormalTok{ base64.b64encode(image_file.read())}

\KeywordTok{def}\NormalTok{ image_request(image_path):}

\NormalTok{    payload }\OperatorTok{=} \StringTok{'\{}\CharTok{\textbackslash{}"}\StringTok{requests}\CharTok{\textbackslash{}"}\StringTok{:[\{}\CharTok{\textbackslash{}"}\StringTok{image}\CharTok{\textbackslash{}"}\StringTok{:\{}\CharTok{\textbackslash{}"}\StringTok{content}\CharTok{\textbackslash{}"}\StringTok{:}\CharTok{\textbackslash{}"}\StringTok{'}\OperatorTok{+}
\NormalTok{    encode_image(image_path).decode(}\StringTok{'utf-8'}\NormalTok{)}\OperatorTok{+}
    \CommentTok{'"\},}\CharTok{\textbackslash{}"}\CommentTok{features}\CharTok{\textbackslash{}"}\CommentTok{:[\{}\CharTok{\textbackslash{}"}\CommentTok{type}\CharTok{\textbackslash{}"}\CommentTok{:}\CharTok{\textbackslash{}"}\CommentTok{TEXT_DETECTION}\CharTok{\textbackslash{}"}\CommentTok{\}]\}]\}'}

\NormalTok{    response }\OperatorTok{=}\NormalTok{ requests.request(}\StringTok{"POST"}\NormalTok{, url, data}\OperatorTok{=}\NormalTok{payload, headers}\OperatorTok{=}\NormalTok{headers, params}\OperatorTok{=}\NormalTok{querystring)}

    \ControlFlowTok{return}\NormalTok{ ast.literal_eval(response.text)}
\end{Highlighting}
\end{Shaded}

This is an example of the response:

\begin{verbatim}
{'responses': [{'textAnnotations': [{'locale': 'ja',
     'description': '-]\n一\n一本の傘を二人でさすこと。多く男女二人の場合に一あい-えん [哀婉](名) 哀れにやさしいこと。 こと。しん【愛郷心](名) 愛婚の精神。.............名)あいく\n-[製~Q)
     れ]()あ\nの。0子持鮎の願漬。\nあいきょうp®(愛郷](名)生まれ故郷を愛する\nに\nVド\nし
     いこと。叉、その程度。\n信的思想た打破すること。\n',
     'boundingPoly': {'vertices': [{'x': 26, 'y': 21},
       {'x': 1556, 'y': 21},
       {'x': 1556, 'y': 2748},
       {'x': 26, 'y': 2748}]}},
    {'description': '-',
     'boundingPoly': {'vertices': [{'x': 1227, 'y': 686},
       {'x': 1227, 'y': 677},
       {'x': 1262, 'y': 677},
       {'x': 1262, 'y': 686}]}},

       すること。\n'}}]}
           {'description': '誘',
     'boundingPoly': {'vertices': [{'x': 785, 'y': 880},
       {'x': 814, 'y': 880},
       {'x': 814, 'y': 914},
       {'x': 785, 'y': 914}]}},
    {'description': '(',
     'boundingPoly': {'vertices': [{'x': 775, 'y': 916},
       {'x': 814, 'y': 916},
       {'x': 814, 'y': 940},
       {'x': 775, 'y': 940}]}},
    ...],
\end{verbatim}

From the previous example, we can observe that the response returns a
list of nested dictionaries. The first nested dictionary called
\textbf{textAnnotations} consists of a list of nested dictionaries. Each
one of those has a description (character) and boundingPoly (boundaries
of the characters).

\hypertarget{boundingpoly}{%
\subsubsection{BoundingPoly}\label{boundingpoly}}

Each boundingPoly consist of vertices in which the symbol is located.

\hypertarget{region}{%
\paragraph{Region}\label{region}}

Te first object in the nested dictionary contains all identified
characters in the image as well as the boundaries that comprises the
location of those characters. This object can resemble the idea of the
region provided in the Azure's API.

Figure 8 shows the region identified by the API.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/sections.png}
\textbf{Figure 8}

\hypertarget{the-character-boundaries-1}{%
\paragraph{The Character Boundaries}\label{the-character-boundaries-1}}

The remaining objects enclose the boundaries of the characters. As it is
shown in figure 9, each boundingPoly node can include one or more
characters.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/boundaries.png}
\textbf{Figure 9}

\hypertarget{characters-1}{%
\subsubsection{Characters}\label{characters-1}}

Once the bounding boxes are located, each character takes its
corresponding place, as it is shown in figure 10. \textbf{Pending find a
way to plot the text in vertical form to make it readable.}

\begin{figure}
\centering
\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/characters.png}
\caption{image}
\end{figure}

\textbf{Figure 10}

\hypertarget{languagehints}{%
\subsubsection{languageHints}\label{languagehints}}

Google Vision API offers the advantage of including in the request
language hints. It consists of a list of languages the user knows in
advance the image contains. For this study, we run two versions, one
without hints and the other one with a list of two hints, such as
Japanese and English, as the image contains some words in English.

\hypertarget{advantages-and-disadvantages-1}{%
\subsubsection{Advantages and
Disadvantages}\label{advantages-and-disadvantages-1}}

\hypertarget{advantages-1}{%
\paragraph{Advantages}\label{advantages-1}}

Same as the Azure API, this is also easy to use after reading the
documentation. It also offers several examples in different programming
languages using the Google libraries for Python. It gives the
possibility to include languages in advanced as hints, and identifies
the orientation automatically. The response contains an object with all
identified characters in the correct order.

Moreover, the API gives the opportunity to send the image in base64
format or using an internal (google storage) or external URL.

\hypertarget{disadvantages-1}{%
\paragraph{Disadvantages}\label{disadvantages-1}}

\hypertarget{pytesseract---python-library}{%
\subsection{PyTesseract - Python
Library}\label{pytesseract---python-library}}

Python-Tesseract is an optical character recognition (OCR) library for
python. It is a wrapper for Google's Tesseract-OCR Engine. PyTesseract
can read all image types such as png, jpeg, gif, tiff, BMP, among
others. It is widely used to process everything from scanned documents.
This inbuilt library of python performs the OCR techniques on the image
to produce the digitized output text in a readable and editable form.

To use this library, we need to install Tesseract. For this study, we
use version 4. IT is necessary to call the .exe file to use Tesseract
with PyTesseract. See the following example.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{#Call .exe location for Windows}
\NormalTok{pytesseract.pytesseract.tesseract_cmd }\OperatorTok{=} \VerbatimStringTok{r'C:\textbackslash{}Program Files\textbackslash{}Tesseract-OCR\textbackslash{}tesseract.exe'} 
\end{Highlighting}
\end{Shaded}

Along with the PyTesseract library, the following libraries are used.

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ PIL }\ImportTok{import}\NormalTok{ Image}
\ImportTok{from}\NormalTok{ PIL }\ImportTok{import}\NormalTok{ ImageOps}
\ImportTok{import}\NormalTok{ pytesseract}
\ImportTok{from}\NormalTok{ os }\ImportTok{import}\NormalTok{ path}
\ImportTok{import}\NormalTok{ pandas }\ImportTok{as}\NormalTok{ pd}
\ImportTok{import}\NormalTok{ matplotlib.pyplot }\ImportTok{as}\NormalTok{ plt}
\ImportTok{from}\NormalTok{ matplotlib.patches }\ImportTok{import}\NormalTok{ Rectangle}
\end{Highlighting}
\end{Shaded}

PyTesseract offers several methods with different outputs when
processing an image to extract text. According to Pypi.org, the uses of
those methods are:

\begin{itemize}
\tightlist
\item
  \textbf{image\_to\_string:} Returns the result of a Tesseract OCR run
  on the image to string
\item
  \textbf{image\_to\_boxes} Returns result containing recognized
  characters and their box boundaries
\item
  \textbf{image\_to\_data:} Returns result containing box boundaries,
  confidences, and other information. Requires Tesseract 3.05+. For more
  information, please check the Tesseract TSV documentation
\item
  \textbf{image\_to\_osd:} Returns result containing information about
  orientation and script detection.
\item
  \textbf{image\_to\_alto\_xml:} Returns result in the form of
  Tesseract's ALTO XML format.
\item
  \textbf{run\_and\_get\_output:} Returns the raw output from Tesseract
  OCR. Gives a bit more control over the parameters that are sent to
  tesseract.
\end{itemize}

For this analysis, we use the method image\_to\_data as this offers the
boundaries and the recognized characters in a handy form so we can
understand the process. Furthermore, in PyTesseract, it is needed to
specify the language in advance. Since PyTesseract is a wrapper of
Google's Tesseract-OCR Engine, Tesseract-OCR must have installed all
required languages. In this case, it is Japanese, which is not included
in its out-of-the-box version. To include a new language, adding the
\textbf{.traineddata} file into the Tesseract-OCR/tessdata folder is
sufficient. However, since the text in the image is vertical Japanese.
It is necessary to include two files: jpn.traineddata and
jpn\_vert.traineddata. Once the files are located correctly, the
following code extracts the text from the image.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{img1 }\OperatorTok{=}\NormalTok{ Image.}\BuiltInTok{open}\NormalTok{(}\VerbatimStringTok{r'~\textbackslash{}inputs\textbackslash{}00-sample-pages_1.png'}\NormalTok{)}
\NormalTok{image_to_data }\OperatorTok{=}\NormalTok{ pytesseract.image_to_data(img1, lang }\OperatorTok{=} \StringTok{'jpn_vert'}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

The output from the previous code converted into a pandas dataframe is
shown in figure 11.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure11.png}
\textbf{Figure 11}

From figure 11, we can observe that the output in the column
\textbf{level} generates five levels. Those are pages, blocks,
paragraphs, lines, and words (characters). Each one is subsets of the
previous one.

\hypertarget{page}{%
\subsubsection{Page}\label{page}}

For this example, the page resembles the concept of region, which is the
largest area of the image enclosing all recognized characters. Figure 12
illustrates the page area.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/page.png}
\textbf{Figure 12}

\hypertarget{blocks}{%
\subsubsection{Blocks}\label{blocks}}

The blocks are subsets of the page area that consist of small groups of
recognized characters. In figure 13, we can see that most of the blocks
are well ordered. In terms of correctness of the boundaries, we can see
that some of them overlap several characters that are not recognized by
the library.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/blocks.png}
\textbf{Figure 13}

\hypertarget{paragraphs}{%
\subsubsection{Paragraphs}\label{paragraphs}}

Similar to the blocks, the paragraphs are subsets of blocks. These
follow the same idea of subareas containing a set of characters. In this
case, for example, we can look at paragraphs five and six, which are
subsets of block five. It is interesting to see how the only paragraph
(21) of block 12 is a smaller area compared to the block. This situation
happens in several other blocks. See figure 14 for a better
understanding.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/paragraphs.png}
\textbf{Figure 14}

\hypertarget{lines-1}{%
\subsubsection{Lines}\label{lines-1}}

Once the paragraphs are defined, the library provides in figure 15, the
last subsets of characters called Lines. From the example, we can see
that most of the characters are located in one of the lines. However,
several others are not. Some of those cases are curious since there is
no clear reason why those characters are not included. For instance,
between the lines 65 and 66, two clear lines are not recognized by the
library.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/lines.png}\\
\textbf{Figure 15}

\hypertarget{character-boundaries}{%
\subsubsection{Character Boundaries}\label{character-boundaries}}

These boundaries enclose the characters. Figure 16 shows that a
character boundary can include one or more characters. However, some
character boundaries overlap with other ones. Moreover, the same as the
previous areas, several characters have been skipped with no apparent
reason.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/boundaries.png}\\
\textbf{Figure 16}

\hypertarget{characters-2}{%
\subsubsection{Characters}\label{characters-2}}

In terms of character-level recognition, we can observe that many
characters are not recognized. Interestingly those characters are in a
correct block, paragraph, line, and character boundary, but it was
skipped. For example, in the first line and the first character boundary
of this line, there are two words, but one of them is not recognized.
Figure 17 illustrates this case.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/characters.png}\\
\textbf{Figure 17}

\hypertarget{advantages-and-disadvantages-2}{%
\subsubsection{Advantages and
Disadvantages}\label{advantages-and-disadvantages-2}}

\hypertarget{advantages-2}{%
\paragraph{Advantages}\label{advantages-2}}

The most important advantage is that this is a free library. It is also
a wrapper from Google's Tesseract Engine. Moreover, the way it presents
the covered areas are very detailed. It offers blocks, paragraphs,
lines, boundaries, and finally the character level.

\hypertarget{disadvantages-2}{%
\paragraph{Disadvantages}\label{disadvantages-2}}

Some lines were completely ignored by Pyteseract, even thought it was
clear enough to be recognized by the tool.

\hypertarget{kindai-ocr}{%
\subsection{Kindai-OCR}\label{kindai-ocr}}

According to the Center for Open Data in the Humanities, Kindai-OCR is
an OCR system for modern Japanese documents. It was built under the N2I
project that study state-of-the-art statistical models for OCR, and work
on the development of infrastructure and providing open access to data.
The datasets were constructed by the University of Tokyo Center for
Education and Research and the National Institute of Japanese Language
and are used for OCR machine learning. These datasets are commonly known
as the Modern Magazine Datasets.

The Kindai-OCR code was developed in Python and released as an open
source code in August 2020 on Github..The Github folder contains all the
necessary code and instructions to assess the OCR tool. \textbf{{[}not
sure if it is necessary to mention the modification in the file test.py,
in order to run the model using GPUs.{]}}

After running the Kindai-OCR for our samples, the system generated three
outputs. They are explained as follows:

\hypertarget{file-result.xml}{%
\subsubsection{File result.xml}\label{file-result.xml}}

This file is presented in an Extensible Markup Language (XML) format
containing a tree with the identified lines, as well as the
corresponding characters. An example of the is shown as follows:

\begin{verbatim}
<?xml version='1.0' encoding='Shift_JIS'?>
<paper xmlns="http://codh.rois.ac.jp/modern-magazine/"><page dpi="100" file="00-sample_pages_3_sec_3.png" height="1040" number="1" width="2430"><line height="905" width="72" x="332" y="0">あいくるし發路事、愛くるし（形、</line><line height="1026" width="76" x="466" y="0">あいくち島（合巳。名。あれせも。ものよ</line><line height="1026" width="69" x="592" y="0">あいくすりし（（きき」名その人の爲に信身あ</line><line height="1031" width="65" x="660" y="0">あいきん（及兵」（名起しい得をうつし表しした</line><line height="1031" width="78" x="778" y="0">あいきん愛心。名客する東なふする、</line><line height="361" width="72" x="849" y="0">あいきよう對</line><line height="292" width="64" x="918" y="0">あいきよう</line><line height="1031" width="64" x="981" y="0">あいきよう對（愛婦（名（（（らきささ。（（彼。。</line><line height="292" width="64" x="2264" y="0">あいきまう</line><line height="997" width="69" x="1749" y="34">（愛教商）名」名毎金。造。。愛もがなてては立</line><line height="337" width="55" x="286" y="38">府がはゆらしい。</line><line height="930" width="68" x="407" y="38">くあふ人。○つばのない兌。。ヒ直。九五五五。</line>
\end{verbatim}

\hypertarget{kraken---python-library}{%
\subsection{Kraken - Python Library}\label{kraken---python-library}}

Kraken is a python library created by Benjamin Kiessling from Université
PSL in France and Leipzig University. This library is a combination of a
fork (independent development built on an existing one) from the Ocropus
package and CLSTM neural network library. Its purpose was to improve
accuracy and performance rates compared with Ocropus. It has been tested
with languages such as Arabic, Persian, Syriac Polytonic Greek, Latin,
among other. However, there is no information about japanese-trained
models.

To assess the performance of this library, it is necessary to train a
model for japanese texts. To do that, Kraken offers a function called
\textbf{train}. This function expects a series of images that according
to Kraken´s website, these images must be high quality scans, preferably
color or grayscale, and at least 300dpi. Images in PDF format are not
allowed. Each image must be accompanied with a text file with extension
.gt.txt. This file will contain the character(s) that corresponds to the
image with the same name. For instance in figure xx we see the image
file is called \textbf{sec1\_line1.png}, the pair-wise text element for
this image is \textbf{sec\_line.gt.txt}.

\includegraphics{E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure18.png}\\
\textbf{Figure 18}

After the training stage, Kraken analyses the layout and extracts text
lines from an input image for later processing by the recognition. A
step by step process is provided by Kraken´s website
(\url{http://kraken.re/index.html}) to recognize text from an image
using the model we want.

\hypertarget{training-process-challenges}{%
\subsubsection{Training process
challenges}\label{training-process-challenges}}

The training process itself is very friendly. However, the data
preparation is the most important part as it generates the samples we
feed into the model. Other studies pointed out that for languages such
as Arabic, at least 800 lines are required to train a descent model. For
the Japanese text of this study we trained 36 lines in which several
characters appear more than once. The result after the training process
was not good, indicating that the need of greater sample data might be
needed which is not in the scope of this study.

\hypertarget{other-limitations}{%
\section{Other limitations}\label{other-limitations}}

In order to use this library it is required to have either Linux or Mac.
In this study, we use Google Colab which is offers a Linux environment
to assess the library.

\hypertarget{amazon-textract}{%
\subsection{Amazon Textract}\label{amazon-textract}}

According to Amazon's website, Amazon Textract can detect Latin-script
characters from the standard English alphabet and ASCII symbols.

\url{https://aws.amazon.com/textract/faqs/}

\hypertarget{amazon-rekognition}{%
\subsection{Amazon Rekognition}\label{amazon-rekognition}}

According to Amazon's website, Amazon Rekognition supports text in most
Latin scripts and numbers. Text detection recognizes up to 50 sequences
of characters per the image or video frame and lists them as words and
lines.

\url{https://aws.amazon.com/rekognition/faqs/}

\hypertarget{evaluation}{%
\section{Evaluation}\label{evaluation}}

For each option, we rank them based on two scales: results and
difficulty. We need to work out a definition for each of these.

Diego's comment: From what I learned so far, it could be easiness (an
API is more straightforward than a library), number of characters
correctly recognized, flexibility (the opposite of easiness), and cost.
Moreover, some APIs such as Google's groups more than one character,
whereas Azure returns only one character per boundary.

In terms of flexibility\ldots{}

Sequence of the characters\ldots{}

Output given\ldots xml, json, flat file, csv\ldots{}

NUmber of characters well recognized\ldots(Accuracy)

The main aspect of the end product will be a graph with two axis, and
dots for where each service is positioned, coloured or faceted by the
test.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\hypertarget{references}{%
\section{References}\label{references}}

1:
\url{https://www.researchgate.net/publication/267465115_An_Overview_and_Applications_of_Optical_Character_Recognition}

2:
\url{https://books-scholarsportal-info.myaccess.library.utoronto.ca/en/read?id=/ebooks/ebooks2/wiley/2011-12-13/1/9780470176535}

3:

4:
\url{https://docs.microsoft.com/en-us/azure/cognitive-services/computer-vision/home}

5:
\url{https://docs.microsoft.com/en-us/azure/cognitive-services/computer-vision/quickstarts/python-print-text}

6: \url{https://cloud.google.com/vision/docs/ocr}

7: \url{https://pypi.org/project/pytesseract/}

8: \url{https://github.com/tesseract-ocr/tessdata}

9: \url{https://github.com/UB-Mannheim/tesseract/wiki}

10: \url{http://codh.rois.ac.jp/software/kindai-ocr/}

11: \url{https://github.com/ducanh841988/Kindai-OCR}

12: Anh Duc Le, Daichi Mochihashi, Katsuya Masuda, Hideki Mima, and Nam
Tuan Ly. 2019. Recognition of Japanese historical text lines by an
attention-based encoder-decoder and text line generation. In Proceedings
of the 5th International Workshop on Historical Document Imaging and
Processing (HIP '19). Association for Computing Machinery, New York, NY,
USA, 37--41. \url{DOI:https://doi.org/10.1145/3352631.3352641}

\end{document}

### 2020-12-03 outputs/documents/paper.Rmd
Text cleaning

@@
 For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the selected OCR tools.
-This image contains 3293 characters.
+The image contains 3293 characters.
 Words in English were counted as one character for this analysis.
@@
 This is important since it is expected to obtain from each OCR tool the correct sequence of characters.
-FOr instance, from section 1 in figure xx, the first five characters from the first line are **[一本の傘を]**
+For instance, from section 1 in figure xx, the first five characters from the first line are **[一本の傘を]**.
+We expect to see the same sequence from each OCR tool.
 
@@
 Those services comprise object detection of an image, visual features tagging, image categorization, Optical Character Recognition (OCR), among $others^4$.
-The OCR API processes an image and returns the language of the document, orientation, regions, lines, and finally, the characters.
+The OCR API processes an image and returns the language of the document, orientation, regions, lines, boundaries, and finally, the characters.
 
@@
 
-Figure 1 presents a sample that corresponds to the section 1 of the image containing Japanese text, but it also contains English text in some fragments of the text.
+Figure xx presents a sample that corresponds to the section 1 of the image containing Japanese text, but it also includes English text in some fragments of the text.
 The API offers the possibility to do self-detection, which in this case is helpful, but also the opportunity to specify the language in advance.
@@
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/section1.png)
-**Figure 1**
+**Figure xx**
 
@@
 
-The blue line figure 2 denotes the segment from the image that includes the characters.
+The blue line figure xx denotes the segment from the image that includes the characters.
 In this example, there is only one blue line because the document is only text.
@@
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/region-section1.png)
- **Figure 2**
+ **Figure xx**
 
@@
 
-Once the region is defined, the API provides in figure 3 (red rectangles) the subsets of characters of the region called Lines.
+Once the region is defined, the API provides in figure xx (red rectangles) the subsets of characters of the region called Lines.
 From the example, we can see that some characters are not included in any of the lines.
@@
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/lines-section1.png)   
- **Figure 3**
+ **Figure xx**
 
@@
 
-After the lines are identified, the API provides in figure 4 each recognized character bounding boxes. Those without a yellow square were not recognized by the API in this example.
+After the lines are identified, the API provides in figure xx each recognized character bounding boxes (yellow regions). Those without a yellow square were not recognized by the API in this example.
 
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/boundaries-section1.png)
- **Figure 4**
+ **Figure xx**
 
@@
 
-Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure 5.
+Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure xx.
 
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/characters-section1.png)
- **Figure 5**
+ **Figure xx**
 
@@
 Even though the API offers the possibility to self-detect the language, It changes the order in which the characters should be in the output.
-In figures 6 we can see that the first line provided by the self-detection approach is located in the middle.
+In figure xx we can see that the first line provided by the self-detection approach is located in the middle.
 This situation does not allow a correct interpretation of the text because it does not follow the reading pattern.
@@
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/self-detection.png)
- **Figure 6**
+ **Figure xx**
 
-When the parameter language is stated as Japanese since the beginning, as we can see in figure 7, it recognizes the first line correctly.
+When the parameter language is stated as Japanese since the beginning, as we can observe in figure xx, it recognizes the first line correctly.
 
@@
 The following example illustrates how to state the headers and parameter, but also create two functions.
-The first one, called encode_image converts an image into base64, an encoding process designed to carry data stored in binary formats across channels that only reliably support text content.
+The first one, called encode_image converts an image into base64 format, an encoding process designed to carry data stored in binary formats across channels that only reliably support text content.
 It can embed image files or other binary assets inside textual assets.
@@
 From the previous example, we can observe that the response returns a list of nested dictionaries.
-The first nested dictionary called **textAnnotations** consists of a list of nested dictionaries.
+The first nested dictionary called **textAnnotations** consists of a list of dictionaries.
 Each one of those has a description (character) and boundingPoly (boundaries of the characters).
@@
 
-Figure 8 shows the region identified by the API.
+Figure xx shows the region identified by the API.
 
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/sections.png)
- **Figure 8**
+ **Figure xx**
 
@@
 
-The remaining objects enclose the boundaries of the characters. As it is shown in figure 9, each boundingPoly node can include one or more characters.
+The remaining objects enclose the boundaries of the characters. As it is shown in figure xx, each boundingPoly node can include one or more characters.
 
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/boundaries.png)
-**Figure 9**
+**Figure xx**
 
@@
 
-Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure 10. **Pending find a way to plot the text in vertical form to make it readable.**
+Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure xx. **Pending find a way to plot the text in vertical form to make it readable.**
 
@@
 
-**Figure 10**
+**Figure xx**
 
@@
 For this study, we run two versions, one without hints and the other one with a list of two hints, such as Japanese and English, as the image contains some words in English.
+Both versions returned the same output.
 
@@
 #### Disadvantages
+
+Unlike Azure Cognitive Services, which returns each recognized character individually, Google Vision groups characters in some cases.
+This situation adds some degree of complexity when processin the response from the API.
+**[Not sure if it is a disadvantage in real life]**
 

### 2020-12-03 outputs/documents/paper.Rmd
Text cleaning

@@
 Unlike Azure Cognitive Services, which returns each recognized character individually, Google Vision groups characters in some cases.
-This situation adds some degree of complexity when processin the response from the API.
+This situation adds some degree of complexity when processing the response from the API.
 **[Not sure if it is a disadvantage in real life]**
@@
 It is widely used to process everything from scanned documents.
-This inbuilt library of python performs the OCR techniques on the image to produce the digitized output text in a readable and editable form.
+This inbuilt python library performs the OCR techniques on the image to produce the digitized output text in a readable and editable form.
 
@@
 
-The output from the previous code converted into a pandas dataframe is shown in figure 11.
+The output from the previous code converted into a pandas dataframe is shown in figure xx.
 
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure11.png)
-**Figure 11**
+**Figure xx**
 
-From figure 11, we can observe that the output in the column **level** generates five levels.
+From figure xx, we can observe that the output in the column **level** generates five levels.
 Those are pages, blocks, paragraphs, lines, and words (characters).
-Each one is subsets of the previous one.
+Each one is a subset of the previous one.
 
@@
 These follow the same idea of subareas containing a set of characters.
-In this case, for example, we can look at paragraphs five and six, which are subsets of block five.
-It is interesting to see how the only paragraph (21) of block 12 is a smaller area compared to the block.
+In this case, for example, we can look at paragraphs three and four, which are subsets of block four (figure xx).
+It is interesting to see how the only paragraph four of block four is a very small area compared to its parent block.
 This situation happens in several other blocks.
-See figure 14 for a better understanding.
+See figure xx for a better understanding.
 
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/paragraphs.png)
-**Figure 14**
+**Figure xx**
 
@@
 
-Once the paragraphs are defined, the library provides in figure 15, the last subsets of characters called Lines.
+Once the paragraphs are defined, the library provides in figure xx, the last subsets of characters called Lines.
 From the example, we can see that most of the characters are located in one of the lines.
 However, several others are not.
-Some of those cases are curious since there is no clear reason why those characters are not included.
-For instance, between the lines 65 and 66, two clear lines are not recognized by the library.
+For some cases there is no clear reason why those characters are not included.
+For instance, between the lines 14 and 15, two clear lines are not recognized by the library.
 
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/lines.png)   
- **Figure 15**
+ **Figure xx**
 
@@
 These boundaries enclose the characters.
-Figure 16 shows that a character boundary can include one or more characters.
-However, some character boundaries overlap with other ones.
-Moreover, the same as the previous areas, several characters have been skipped with no apparent reason.
+Figure xx shows that a character boundary can include one or more characters.
+However, some character boundaries overlap each other.
+Moreover, same as the previous areas, several characters have been skipped with no apparent reason.
 
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/boundaries.png)   
- **Figure 16**
+ **Figure xx**
 
@@
 Interestingly those characters are in a correct block, paragraph, line, and character boundary, but it was skipped.
-For example, in the first line and the first character boundary of this line, there are two words, but one of them is not recognized.
-Figure 17 illustrates this case.
+For example, in the first line of recognized characters and the first character boundary of this line, there are two words, but one of them is not recognized.
+Figure xx illustrates this case.
 
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/characters.png)   
- **Figure 17**
+ **Figure xx**
 
@@
 
-Some lines were completely ignored by Pyteseract, even thought it was clear enough to be recognized by the tool.
+Some lines were completely ignored by Pyteseract, even thought it was clear enough to be recognized by the tool. Moreover, same as Google Vision, this library groups more than one character sometimes.
 
@@
 
-The Kindai-OCR code was developed in Python and released as an open source code in August 2020 on Github..The Github folder contains all the necessary code and instructions to assess the OCR tool.
-**[not sure if it is necessary to mention the modification in the file test.py, in order to run the model using GPUs.]**
+The Kindai-OCR code was developed in Python and released as an open source code in August 2020 on Github.
+The Github folder contains all the necessary code and instructions to assess the OCR tool.
+**[not sure if it is necessary to mention the modification in the file test.py I did, in order to run the model using GPUs.]**
 
@@
 
-This file is presented in an Extensible Markup Language (XML) format containing a tree with the identified lines, as well as the corresponding characters. An example of the is shown as follows:
+This file is presented in an Extensible Markup Language (XML) format containing a tree with the identified lines, as well as the corresponding characters.
+An example of the xml file is shown as follows:
 
@@
 Moreover, the recognition process is very easy.
-To obtain results just by putting the images in the test folder and running the file called test.py on Python is enough to obtain the results.
+To obtain results, just by putting the images in the test folder and running the file called test.py on Python is enough to obtain the results.
 
@@
 
-At the time of this assessment, the use of GPUs is required which is a limitation to take into account. For this study, we used Colab from Google, which offers this capability.
+At the time of this assessment, the use of GPUs is required which is a limitation to take into account.
+For this study, we used Colab from Google, which offers this capability.
+Moreover, Kindai-OCR returns the characters grouped by lines.
+They are not generated individually.
 
@@
 Each image must be accompanied with a text file with extension .gt.txt.
-This file will contain the character(s) that corresponds to the image with the same name.
-For instance in figure xx we see the image file is called **sec1_line1.png**, the pair-wise text element for this image is **sec_line.gt.txt**.
+This file will contain the character(s) that correspond(s) to the image with the same name.
+For instance in figure xx we see the image file is called **sec1_line1.png**, the pair-wise text element for this image is **sec1_line1.gt.txt**.
 
 ![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure18.png)   
- **Figure 18**
+ **Figure xx**
 
@@
 For the Japanese text of this study we trained 36 lines in which several characters appear more than once.
-The result after the training process was not good, indicating that the need of greater sample data might be needed which is not in the scope of this study.
+The result after the training process was not good, indicating that the need of greater sample data is needed, which is not in the scope of this study.
 
@@
 
-In order to use this library it is required to have either Linux or Mac. In this study, we use Google Colab which is offers a Linux environment to assess the library.
+In order to use this library it is required to have either Linux or Mac. In this study, we use Google Colab which offers a Linux environment to assess the library.
 
@@
 
-Diego's comment: From what I learned so far, it could be easiness (an API is more straightforward than a library), number of characters correctly recognized, flexibility (the opposite of easiness), and cost.
+Diego's comment: From what I learned so far, it could be easiness (an API is more straightforward than a library), number of characters correctly recognized, flexibility, and cost.
 Moreover, some APIs such as Google's groups more than one character, whereas Azure returns only one character per boundary.

### 2020-12-03 outputs/documents/paper.Rmd
PDF version

@@
 
-![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/outputs/documents/sections.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/sections.png)
 **Figure XX**
@@
 
-![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_1.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped%20pages/00-sample_pages_3_sec_1.png)
 **Figure XX Section 1**
 
-![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_2.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_2.png)
 **Figure XX Section 2**
 
-![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_3.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_3.png)
 **Figure XX Section 3**
 
-![image](https://raw.githubusercontent.com/RohanAlexander/japanese_dictionaries/master/inputs/cropped%20pages/00-sample_pages_3_sec_4.png)
+![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_4.png)
 **Figure XX Section 4**
@@
 
-NUmber of characters well recognized...(Accuracy)
+Number of characters well recognized...(Accuracy)
 

### 2020-12-08 outputs/documents/paper.Rmd
Reorganize directory and begin updating paper

@@
 author: "Rohan Alexander, John Tang, Diego Mamanche Castellanos"
-date: "08 August 2020"
+date: "8 December 2020"
+abstract: "TBD"
 output:
@@
   html_document: default
+bibliography: references.bib
 ---
@@
 
-A crucial aspect of the data science workflow is gathering data.
-It involves the tools and methods used to collect information in an established systematic fashion and identify the variables being measured.
-It also describes the methods used to obtain the data.
-Although the data collection component of research remains the same regardless of the field of study, the methods used vary among those fields of study as they have different interests.
-Moreover, the diversity of data types adds complexity to the process of gathering data.
-Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset.
+A crucial step in the data analysis workflow is gathering data.
+This step involves tools and methods to collect raw data in an systematic way.
+In this paper we are interested in gathering data from Portable Document Format (PDF) files, in particular, when these PDFs were created by scans, and hence must be processed before their data can be analysed.
+Such PDF files are unstructured data, meaning that the data are not tagged and are not organised in a regular way.^[Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset.
 Some examples are tables and relations.
@@
 name = "Bob" but also other markers to separate semantic elements and enforce hierarchies of records and fields within the data.
-Finally, Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags.
-However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data $(Robert M.
-Losee, 2005)^1$.
-This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.
+Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags.
+However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data [@Losee2006].
+This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags could be assigned manually, typically a statistical model is used for reasons of efficiency, and this process is called Optical Character Recognition (OCR).
+We evaluate several pre-trained commercial OCR options accessed via APIs: 1) X, 2), and 3), ; additionally several OCR options that are run locally: 4) X, 5), and 6), ; and finally 7) training our own model.
+We find...
+**[TBD]**.
 
-The Portable Document Format (PDF) is an example of unstructured data created by the company Adobe in the 90s.
-It is widely used for documents.
-According to the $ISO 32000-2:2017^2$, the latest edition of the PDF Reference (2.0), PDF enables users to exchange and view electronic documents easily and reliably, independent of the environment in which they were created or the environment in which they are viewed or printed.
-It is intended to fulfill the following requirements:
+PDF files were developed in 1993 by the technology company Adobe and are useful for documents because they should display in a consistent way independent of the environment that created them or the environment in which they are being viewed.
+One feature of PDFs is that they can include a variety of objects, for instance, text, photos, figures, etc.
+However, this variety can limit the capacity of PDFs to be used directly as data inputs for statistical analysis.
+The data first needs to be extracted from the PDF.
 
-- preservation of document fidelity independent of the device, platform, and software,
-- merging of content from diverse sources — Web sites, word processing and spreadsheet
-programs, scanned documents, photos, and graphics — into one self-contained document while
-maintaining the integrity of all original source documents,
-- an extensible metadata model at the document and object level,
-- collaborative editing of documents from multiple locations or platforms,
-- digital signatures to certify authenticity,
-- security and permissions to allow the creator to retain control of the document and associated
-rights,
-- accessibility of content to those with disabilities,
-- extraction and reuse of content for use with other file formats and applications, and
-- electronic forms to gather and/or represent data within business systems.
+Sometimes it is possible to copy and paste the data from the PDF.
+This is more likely when the PDF only contains simple text or regular tables.
+In particular, if the PDF has been created by an application such as Word then often the text can be extracted in this way because they are stored as text.
+But it is not as easy if the text has been stored as an image which is then part of the PDF
 
-To mention some of the features incorporated in this version we have:
-
-- 12.10, "Geospatial features";
-- 13.7, "Rich media" annotations;
-- 14.7.4, "Namespaces" for tagged PDF;
-- 14.9.6, "Pronunciation hints";
-- 14.12, "Document parts";
-- 14.13, "Associated files";
-- Support for PRC (see 13.6, "3D Artwork");
-- Support for UTF-8.
-
-However, these advantages mean that the data in PDFs cannot be used for quantitative statistical analysis.
-The reason is that it needs measurable and verifiable data.
-But PDF documents, as it was mentioned previously, can have different objects, some of them non-static objects compressed in the same document.
-This situation makes it difficult to extract valuable information from the paper.
-
-Sometimes just by copying and pasting the information directly from the PDF is possible when it contains simple texts or regular tables.
-In that case, there is no barrier in the process of extracting data.
-But other times it is not as easy if it is an image, a survey form, or complex shapes containing relevant information.
 Furthermore, there is a linguistic component that adds more complexity.
-For instance, it is well known that non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process.
-It is because those characters have complicated structures, a huge number of categories, and resemblance among characters, font unevenness, or writing styles.
+For instance, it is well known that non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[ADD CITE]**.
+It is because those characters have complicated structures, a large number of categories (for instance, compare the 26 characters in the English alphabet with the thousands of characters in Japanese kanji), and resemblance among characters, font unevenness, or writing styles.
 In those cases, the need for reliable tools or methods with the ability to elicit data becomes extremely important.
 
-Optical character recognition (OCR), a process that transforms a bitmapped image of printed or handwritten text into text code, and thereby making it machine-readable, has been widely used for scientists trying to capture the images of characters and texts back in the 50s.
-First, by mechanical and optical means of rotating disks and photomultiplier flying spot scanner with a cathode ray tube lens, followed by photocells and arrays of them.
+Optical character recognition (OCR),is a process that transforms a bitmapped image of printed or handwritten text into text code **[ADD CITE]**.
+It thereby becomes machine-readable.
+It has been used to parse images of characters since the 1950s **[ADD CITE]**.
+These initial approaches used mechanical and optical means of rotating disks and photomultiplier flying spot scanner with a cathode ray tube lens, followed by photocells and arrays of them **[ADD CITE]**.
 The OCR process was slow, and one line of characters could be digitized at a time.
-Nowadays, in OCR, once a printed or handwritten text has been captured optically by a scanner or some other optical means, the digital image goes through the following stages of a computer recognition system $(Cheriet, Mohamed; Kharma, 2007)^3$:
+These days once a printed or handwritten text has been captured optically by a scanner or some other optical means, the digital image goes through the following stages of a computer recognition system [@Cheriet2007]:
 
@@
 In this paper we review various OCR options for researchers who need to gather data from PDFs in which the text must be extracted to be reused, edited, or reformatted; the text should be available for full-text information retrieval; the text is to be coded in HTML or SGML; the text should be available to adaptive equipment for the visually impaired; the file size is of concern (in terms of storage or bandwidth to transmit); or the resources are available to perform OCR and correct the output.
+
+Although this step remains the same regardless of the field of study, the methods used vary between those fields of study because of their different interests.
+Moreover, the diversity of data types adds complexity to the process of gathering data.
 
@@
 Words in English were counted as one character for this analysis.
-MOreover, the sample text was divided into four images called **sections** as it is illustrated in figure XX.
+MOreover, the sample text was divided into four images called **sections** as illustrated in Figure \@ref(fig:sections).
 These new images were assessed across all OCR tools.
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/sections.png)
-**Figure XX**
+```{r sections, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/sections.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped%20pages/00-sample_pages_3_sec_1.png)
-**Figure XX Section 1**
+```{r section1, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_1.png"))
+```
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_2.png)
-**Figure XX Section 2**
+```{r section2, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_2.png"))
+```
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_3.png)
-**Figure XX Section 3**
+```{r section3, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_3.png"))
+```
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/inputs/cropped pages/00-sample_pages_3_sec_4.png)
-**Figure XX Section 4**
+```{r section4, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_4.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/section1.png)
-**Figure xx**
+```{r azuresection1, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/azure-images/section1.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/region-section1.png)
- **Figure xx**
+```{r azureregionsection1, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/azure-images/region-section1.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/lines-section1.png)   
- **Figure xx**
+```{r azureregionsection2, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/azure-images/lines-section1.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/boundaries-section1.png)
- **Figure xx**
+```{r azureregionsection3, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/azure-images/boundaries-section1.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/characters-section1.png)
- **Figure xx**
+```{r azureregionsection4, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/azure-images/characters-section1.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/self-detection.png)
- **Figure xx**
+```{r azureregionsection5, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/azure-images/self-detection.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/japanese-parameter.png)
- **Figure 7**
+```{r azureregionsection6, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/azure-images/japanese-parameter.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/sections.png)
- **Figure xx**
+```{r azureregionsection7, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/google-images/sections.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/boundaries.png)
-**Figure xx**
+```{r azureregionsection8, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/google-images/boundaries.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/characters.png)
-
-**Figure xx**
+```{r azureregionsection9, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/google-images/characters.png"))
+```
 
@@
 
-To use this library, we need to install Tesseract. For this study, we use version 4. IT is necessary to call the .exe file to use Tesseract with PyTesseract. See the following example.
+To use this library, we need to install Tesseract. For this study, we use version 4. It is necessary to call the .exe file to use Tesseract with PyTesseract. See the following example.
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure11.png)
-**Figure xx**
+```{r azureregionsectio98, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/figure11.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/page.png)
-**Figure 12**
+```{r azureregionsectio12, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/pytesseract-images/page.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/blocks.png)
-**Figure 13**
+```{r azureregionsectio13, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/pytesseract-images/blocks.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/paragraphs.png)
-**Figure xx**
+```{r azureregionsectio14, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/pytesseract-images/paragraphs.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/lines.png)   
- **Figure xx**
+```{r azureregionsectio15, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/pytesseract-images/lines.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/boundaries.png)   
- **Figure xx**
+```{r azureregionsectio16, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/pytesseract-images/boundaries.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/pytesseract-images/characters.png)   
- **Figure xx**
+```{r azureregionsectio17, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/pytesseract-images/characters.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/kindai-images/xml-processed.png)   
- **Figure XX**
+```{r azureregionsectio27, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/kindai-images/xml-processed.png"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/kindai-images/kindai-section1.jpg)
-**Figure XX**
+```{r azureregionsectio47, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/kindai-images/kindai-section1.jpg"))
+```
 
@@
 
-![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure18.png)   
- **Figure xx**
+```{r azureregionsectio18, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
+knitr::include_graphics(here::here("outputs/documents/figure18.png"))
+```
 

### 2020-12-08 api-exploration/kindai-ocr/basenet/vgg16_bn.py

@@ -1,69 +1,0 @@
-from collections import namedtuple
-
-import torch
-from torchvision import models
-from torchvision.models.vgg import model_urls
-from torchutil import *
-import os
-
-weights_folder = os.path.join(os.path.dirname(__file__))
-
-
-class vgg16_bn(torch.nn.Module):
-    def __init__(self, pretrained=True, freeze=False):
-        super(vgg16_bn, self).__init__()
-        model_urls['vgg16_bn'] = model_urls['vgg16_bn'].replace('https://', 'http://')
-        # vgg_pretrained_features = models.vgg16_bn(pretrained=pretrained).features
-        vgg_pretrained_features = models.vgg16_bn(pretrained=False)
-        if pretrained:
-            print('./pretrain/vgg16_bn-6c64b313.pth')
-            vgg_pretrained_features.load_state_dict(
-                copyStateDict(torch.load('./pretrain/vgg16_bn-6c64b313.pth')))
-        vgg_pretrained_features = vgg_pretrained_features.features
-        self.slice1 = torch.nn.Sequential()
-        self.slice2 = torch.nn.Sequential()
-        self.slice3 = torch.nn.Sequential()
-        self.slice4 = torch.nn.Sequential()
-        self.slice5 = torch.nn.Sequential()
-        for x in range(12):  # conv2_2
-            self.slice1.add_module(str(x), vgg_pretrained_features[x])
-        for x in range(12, 19):  # conv3_3
-            self.slice2.add_module(str(x), vgg_pretrained_features[x])
-        for x in range(19, 29):  # conv4_3
-            self.slice3.add_module(str(x), vgg_pretrained_features[x])
-        for x in range(29, 39):  # conv5_3
-            self.slice4.add_module(str(x), vgg_pretrained_features[x])
-
-        # fc6, fc7 without atrous conv
-        self.slice5 = torch.nn.Sequential(
-            nn.MaxPool2d(kernel_size=3, stride=1, padding=1),
-            nn.Conv2d(512, 1024, kernel_size=3, padding=6, dilation=6),
-            nn.Conv2d(1024, 1024, kernel_size=1)
-        )
-
-        if not pretrained:
-            init_weights(self.slice1.modules())
-            init_weights(self.slice2.modules())
-            init_weights(self.slice3.modules())
-            init_weights(self.slice4.modules())
-
[…]

### 2020-12-08 api-exploration/kindai-ocr/craft.py

@@ -1,92 +1,0 @@
-"""  
-Copyright (c) 2019-present NAVER Corp.
-MIT License
-"""
-
-# -*- coding: utf-8 -*-
-import torch
-import torch.nn as nn
-import torch.nn.functional as F
-from collections import OrderedDict
-import torch.nn.init as init
-from torchutil import *
-
-from basenet.vgg16_bn import vgg16_bn
-
-
-class double_conv(nn.Module):
-    def __init__(self, in_ch, mid_ch, out_ch):
-        super(double_conv, self).__init__()
-        self.conv = nn.Sequential(
-            nn.Conv2d(in_ch + mid_ch, mid_ch, kernel_size=1),
-            nn.BatchNorm2d(mid_ch),
-            nn.ReLU(inplace=True),
-            nn.Conv2d(mid_ch, out_ch, kernel_size=3, padding=1),
-            nn.BatchNorm2d(out_ch),
-            nn.ReLU(inplace=True)
-        )
-
-    def forward(self, x):
-        x = self.conv(x)
-        return x
-
-
-class CRAFT(nn.Module):
-    def __init__(self, pretrained=True, freeze=False):
-        super(CRAFT, self).__init__()
-
-        """ Base network """
-        # self.net = vgg16_bn(pretrained, freeze)
-        # self.net.load_state_dict(copyStateDict(torch.load('vgg16_bn-6c64b313.pth')))
-        # self.basenet = self.net
-        self.basenet = vgg16_bn(pretrained, freeze)
-        """ U network """
-        self.upconv1 = double_conv(1024, 512, 256)
-        self.upconv2 = double_conv(512, 256, 128)
-        self.upconv3 = double_conv(256, 128, 64)
-        self.upconv4 = double_conv(128, 64, 32)
-
-        num_class = 2
-        self.conv_cls = nn.Sequential(
-            nn.Conv2d(32, 32, kernel_size=3, padding=1), nn.ReLU(inplace=True),
-            nn.Conv2d(32, 32, kernel_size=3, padding=1), nn.ReLU(inplace=True),
-            nn.Conv2d(32, 16, kernel_size=3, padding=1), nn.ReLU(inplace=True),
-            nn.Conv2d(16, 16, kernel_size=1), nn.ReLU(inplace=True),
-            nn.Conv2d(16, num_class, kernel_size=1),
-        )
-
-        init_weights(self.upconv1.modules())
-        init_weights(self.upconv2.modules())
-        init_weights(self.upconv3.modules())
[…]

### 2020-12-08 api-exploration/kindai-ocr/data_loader.py

@@ -1,718 +1,0 @@
-
-
-
-###for icdar2015####
-
-
-
-import torch
-import torch.utils.data as data
-import scipy.io as scio
-from gaussian import GaussianTransformer
-from watershed import watershed
-import re
-import itertools
-from file_utils import *
-from mep import mep
-import random
-from PIL import Image
-import torchvision.transforms as transforms
-import craft_utils
-import Polygon as plg
-import time
-import numpy
-
-def ratio_area(h, w, box):
-    area = h * w
-    ratio = 0
-    for i in range(len(box)):
-        poly = plg.Polygon(box[i])
-        box_area = poly.area()
-        tem = box_area / area
-        if tem > ratio:
-            ratio = tem
-    return ratio, area
-
-def rescale_img(img, box, h, w):
-    image = np.zeros((768,768,3),dtype = np.uint8)
-    length = max(h, w)
-    scale = 768 / length           ###768 is the train image size
-    img = cv2.resize(img, dsize=None, fx=scale, fy=scale)
-    image[:img.shape[0], :img.shape[1]] = img
-    box *= scale
-    return image
-
-def random_scale(img, bboxes, min_size):
-    h, w = img.shape[0:2]
-    # ratio, _ = ratio_area(h, w, bboxes)
-    # if ratio > 0.5:
-    #     image = rescale_img(img.copy(), bboxes, h, w)
-    #     return image
-    scale = 1.0
-    if max(h, w) > 1280:
-        scale = 1280.0 / max(h, w)
-    random_scale = np.array([0.5, 1.0, 1.5, 2.0])
-    scale1 = np.random.choice(random_scale)
-    if min(h, w) * scale * scale1 <= min_size:
-        scale = (min_size + 10) * 1.0 / min(h, w)
-    else:
-        scale = scale * scale1
-    bboxes *= scale
-    img = cv2.resize(img, dsize=None, fx=scale, fy=scale)
-    return img
-
-def padding_image(image,imgsize):
-    length = max(image.shape[0:2])
-    if len(image.shape) == 3:
-        img = np.zeros((imgsize, imgsize, len(image.shape)), dtype = np.uint8)
-    else:
-        img = np.zeros((imgsize, imgsize), dtype = np.uint8)
-    scale = imgsize / length
-    image = cv2.resize(image, dsize=None, fx=scale, fy=scale)
-    if len(image.shape) == 3:
-        img[:image.shape[0], :image.shape[1], :] = image
-    else:
[…]

### 2020-12-08 api-exploration/kindai-ocr/decoder.py

@@ -1,133 +1,0 @@
-import torch
-import torch.nn as nn
-
-
-# two layers of GRU
-class Gru_cond_layer(nn.Module):
-    def __init__(self, params):
-        super(Gru_cond_layer, self).__init__()
-        self.cuda = params['cuda']
-        # attention
-        self.conv_Ua = nn.Conv2d(params['D'], params['dim_attention'], kernel_size=1)
-        self.fc_Wa = nn.Linear(params['n'], params['dim_attention'], bias=False)
-        self.conv_Q = nn.Conv2d(1, 512, kernel_size=11, bias=False, padding=5)
-        self.fc_Uf = nn.Linear(512, params['dim_attention'])
-        self.fc_va = nn.Linear(params['dim_attention'], 1)
-
-        # the first GRU layer
-        self.fc_Wyz = nn.Linear(params['m'], params['n'])
-        self.fc_Wyr = nn.Linear(params['m'], params['n'])
-        self.fc_Wyh = nn.Linear(params['m'], params['n'])
-
-        self.fc_Uhz = nn.Linear(params['n'], params['n'], bias=False)
-        self.fc_Uhr = nn.Linear(params['n'], params['n'], bias=False)
-        self.fc_Uhh = nn.Linear(params['n'], params['n'], bias=False)
-
-        # the second GRU layer
-        self.fc_Wcz = nn.Linear(params['D'], params['n'], bias=False)
-        self.fc_Wcr = nn.Linear(params['D'], params['n'], bias=False)
-        self.fc_Wch = nn.Linear(params['D'], params['n'], bias=False)
-
-        self.fc_Uhz2 = nn.Linear(params['n'], params['n'])
-        self.fc_Uhr2 = nn.Linear(params['n'], params['n'])
-        self.fc_Uhh2 = nn.Linear(params['n'], params['n'])
-
-    def forward(self, params, embedding, mask=None, context=None, context_mask=None, one_step=False, init_state=None,
-                alpha_past=None):
-        n_steps = embedding.shape[0]
-        n_samples = embedding.shape[1]
-
-        Ua_ctx = self.conv_Ua(context)
-        Ua_ctx = Ua_ctx.permute(2, 3, 0, 1) 
-        state_below_z = self.fc_Wyz(embedding)
-        state_below_r = self.fc_Wyr(embedding)
-        state_below_h = self.fc_Wyh(embedding)
-
-        if one_step:
-            if mask is None:
[…]

### 2020-12-08 api-exploration/kindai-ocr/encoder.py

@@ -1,108 +1,0 @@
-import math
-import torch
-import torch.nn as nn
-import torch.nn.functional as F
-
-
-# DenseNet-B
-class Bottleneck(nn.Module):
-    def __init__(self, nChannels, growthRate, use_dropout):
-        super(Bottleneck, self).__init__()
-        interChannels = 4 * growthRate
-        self.bn1 = nn.BatchNorm2d(interChannels)
-        self.conv1 = nn.Conv2d(nChannels, interChannels, kernel_size=1, bias=False)
-        self.bn2 = nn.BatchNorm2d(growthRate)
-        self.conv2 = nn.Conv2d(interChannels, growthRate, kernel_size=3, padding=1, bias=False)
-        self.use_dropout = use_dropout
-        self.dropout = nn.Dropout(p=0.2)
-
-    def forward(self, x):
-        out = F.relu(self.bn1(self.conv1(x)), inplace=True)
-        if self.use_dropout:
-            out = self.dropout(out)
-        out = F.relu(self.bn2(self.conv2(out)), inplace=True)
-        if self.use_dropout:
-            out = self.dropout(out)
-        out = torch.cat((x, out), 1)
-        return out
-
-
-# single layer
-class SingleLayer(nn.Module):
-    def __init__(self, nChannels, growthRate, use_dropout):
-        super(SingleLayer, self).__init__()
-        self.bn1 = nn.BatchNorm2d(nChannels)
-        self.conv1 = nn.Conv2d(nChannels, growthRate, kernel_size=3, padding=1, bias=False)
-        self.use_dropout = use_dropout
-        self.dropout = nn.Dropout(p=0.2)
-
-    def forward(self, x):
-        out = self.conv1(F.relu(x, inplace=True))
-        if self.use_dropout:
-            out = self.dropout(out)
-        out = torch.cat((x, out), 1)
-        return out
-
-
-# transition layer
-class Transition(nn.Module):
-    def __init__(self, nChannels, nOutChannels, use_dropout):
-        super(Transition, self).__init__()
-        self.bn1 = nn.BatchNorm2d(nOutChannels)
-        self.conv1 = nn.Conv2d(nChannels, nOutChannels, kernel_size=1, bias=False)
-        self.use_dropout = use_dropout
-        self.dropout = nn.Dropout(p=0.2)
-
-    def forward(self, x):
-        out = F.relu(self.bn1(self.conv1(x)), inplace=True)
-        if self.use_dropout:
[…]

### 2020-12-08 api-exploration/kindai-ocr/encoder_decoder.py

@@ -1,101 +1,0 @@
-import torch
-import torch.nn as nn
-import torch.nn.functional as F
-from encoder import DenseNet
-from decoder import Gru_cond_layer, Gru_prob
-
-
-# create gru init state
-class FcLayer(nn.Module):
-    def __init__(self, nin, nout):
-        super(FcLayer, self).__init__()
-        self.fc = nn.Linear(nin, nout)
-
-    def forward(self, x):
-        out = torch.tanh(self.fc(x))
-        return out
-
-
-# Embedding
-class My_Embedding(nn.Module):
-    def __init__(self, params):
-        super(My_Embedding, self).__init__()
-        self.embedding = nn.Embedding(params['K'], params['m'])
-        self.cuda = params['cuda']
-
-    def forward(self, params, y):
-        if y.sum() < 0.: 
-            emb = torch.zeros(1, params['m'])
-            if self.cuda:
-                emb.cuda()
-        else:
-            emb = self.embedding(y)
-            if len(emb.shape) == 3:  # only for training stage
-                emb_shifted = torch.zeros([emb.shape[0], emb.shape[1], params['m']], dtype=torch.float32)
-                if self.cuda:
-                    emb_shifted.cuda()
-                emb_shifted[1:] = emb[:-1]
-                emb = emb_shifted
-        return emb
-
-
-class Encoder_Decoder(nn.Module):
-    def __init__(self, params):
-        super(Encoder_Decoder, self).__init__()
-        self.encoder = DenseNet(growthRate=params['growthRate'], reduction=params['reduction'],
-                                bottleneck=params['bottleneck'], use_dropout=params['use_dropout'])
-        self.init_GRU_model = FcLayer(params['D'], params['n'])
-        self.emb_model = My_Embedding(params)
-        self.gru_model = Gru_cond_layer(params)
-        self.gru_prob_model = Gru_prob(params)
-        self.cuda = params['cuda']
-
-    def forward(self, params, x, x_mask, y, y_mask, one_step=False):
-        # recover permute
-        y = y.permute(1, 0)
-        y_mask = y_mask.permute(1, 0)
-
-        ctx, ctx_mask = self.encoder(x, x_mask)
-
-        # init state
-        ctx_mean = (ctx * ctx_mask[:, None, :, :]).sum(3).sum(2) / ctx_mask.sum(2).sum(1)[:, None]
-        init_state = self.init_GRU_model(ctx_mean)
-
-        # two GRU layers
[…]

### 2020-12-08 api-exploration/kindai-ocr/file_utils.py

@@ -1,84 +1,0 @@
-# -*- coding: utf-8 -*-
-import os
-import numpy as np
-import cv2
-import imgproc
-
-# borrowed from https://github.com/lengstrom/fast-style-transfer/blob/master/src/utils.py
-def get_files(img_dir):
-    imgs, masks, xmls = list_files(img_dir)
-    return imgs, masks, xmls
-
-def list_files(in_path):
-    img_files = []
-    mask_files = []
-    gt_files = []
-    for (dirpath, dirnames, filenames) in os.walk(in_path):
-        for file in filenames:
-            filename, ext = os.path.splitext(file)
-            ext = str.lower(ext)
-            if ext == '.jpg' or ext == '.jpeg' or ext == '.gif' or ext == '.png' or ext == '.pgm':
-                img_files.append(os.path.join(dirpath, file))
-            elif ext == '.bmp':
-                mask_files.append(os.path.join(dirpath, file))
-            elif ext == '.xml' or ext == '.gt' or ext == '.txt':
-                gt_files.append(os.path.join(dirpath, file))
-            elif ext == '.zip':
-                continue
-    # img_files.sort()
-    # mask_files.sort()
-    # gt_files.sort()
-    return img_files, mask_files, gt_files
-
-def saveResult(img_file, img, boxes, dirname='./result/', verticals=None, texts=None):
-        """ save text detection result one by one
-        Args:
-            img_file (str): image file name
-            img (array): raw image context
-            boxes (array): array of result file
-                Shape: [num_detections, 4] for BB output / [num_detections, 4] for QUAD output
-        Return:
-            None
-        """
-        img = np.array(img)
-        #print (np.shape(img))
-        result = np.zeros((np.shape(img)[0], np.shape(img)[1]))
-        # make result file list
-        filename, file_ext = os.path.splitext(os.path.basename(img_file))
-
-        # result directory
-        res_file = dirname + "res_" + filename + '.txt'
-        res_img_file = dirname + "res_" + filename + '.jpg'
-
-        if not os.path.isdir(dirname):
-            os.mkdir(dirname)
-
-        with open(res_file, 'w') as f:
-            for i, box in enumerate(boxes):
-                poly = np.array(box).astype(np.int32).reshape((-1))
-                strResult = ','.join([str(p) for p in poly]) + '\r\n'
-                # poly = np.array(box).astype(np.int32)
[…]

### 2020-12-08 api-exploration/kindai-ocr/gaussian.py

@@ -1,380 +1,0 @@
-from math import exp
-import numpy as np
-import cv2
-import os
-import imgproc
-
-
-class GaussianTransformer(object):
-
-    def __init__(self, imgSize=512, region_threshold=0.4,
-                 affinity_threshold=0.2):
-        distanceRatio = 3.34
-        scaledGaussian = lambda x: exp(-(1 / 2) * (x ** 2))
-        self.region_threshold = region_threshold
-        self.imgSize = imgSize
-        self.standardGaussianHeat = self._gen_gaussian_heatmap(imgSize, distanceRatio)
-
-        _, binary = cv2.threshold(self.standardGaussianHeat, region_threshold * 255, 255, 0)
-        np_contours = np.roll(np.array(np.where(binary != 0)), 1, axis=0).transpose().reshape(-1, 2)
-        x, y, w, h = cv2.boundingRect(np_contours)
-        self.regionbox = np.array([[x, y], [x + w, y], [x + w, y + h], [x, y + h]], dtype=np.int32)
-        # print("regionbox", self.regionbox)
-        _, binary = cv2.threshold(self.standardGaussianHeat, affinity_threshold * 255, 255, 0)
-        np_contours = np.roll(np.array(np.where(binary != 0)), 1, axis=0).transpose().reshape(-1, 2)
-        x, y, w, h = cv2.boundingRect(np_contours)
-        self.affinitybox = np.array([[x, y], [x + w, y], [x + w, y + h], [x, y + h]], dtype=np.int32)
-        # print("affinitybox", self.affinitybox)
-        self.oribox = np.array([[0, 0, 1], [imgSize - 1, 0, 1], [imgSize - 1, imgSize - 1, 1], [0, imgSize - 1, 1]],
-                               dtype=np.int32)
-
-    def _gen_gaussian_heatmap(self, imgSize, distanceRatio):
-        scaledGaussian = lambda x: exp(-(1 / 2) * (x ** 2))
-        heat = np.zeros((imgSize, imgSize), np.uint8)
-        for i in range(imgSize):
-            for j in range(imgSize):
-                distanceFromCenter = np.linalg.norm(np.array([i - imgSize / 2, j - imgSize / 2]))
-                distanceFromCenter = distanceRatio * distanceFromCenter / (imgSize / 2)
-                scaledGaussianProb = scaledGaussian(distanceFromCenter)
-                heat[i, j] = np.clip(scaledGaussianProb * 255, 0, 255)
-        return heat
-
-    def _test(self):
-        sigma = 10
[…]

### 2020-12-08 api-exploration/kindai-ocr/test.py

@@ -1,350 +1,0 @@
-"""  
-Copyright (c) 2019-present NAVER Corp.
-MIT License
-"""
-
-# -*- coding: cp932 -*-
-import sys
-import os
-import time
-import argparse
-
-import torch
-import torch.nn as nn
-import torch.backends.cudnn as cudnn
-from torch.autograd import Variable
-
-from PIL import Image, ImageDraw, ImageFont
-from utils import dataIterator, load_dict, gen_sample, load_mapping
-from encoder_decoder import Encoder_Decoder
-
-import cv2
-from skimage import io
-import numpy as np
-import craft_utils
-import imgproc
-import file_utils
-import json
-import zipfile
-import xml.etree.cElementTree as ET
-import xml.dom.minidom as minidom
-import codecs
-from craft import CRAFT
-
-from collections import OrderedDict
-def copyStateDict(state_dict):
-    if list(state_dict.keys())[0].startswith("module"):
-        start_idx = 1
-    else:
-        start_idx = 0
-    new_state_dict = OrderedDict()
-    for k, v in state_dict.items():
-        name = ".".join(k.split(".")[start_idx:])
-        new_state_dict[name] = v
-    return new_state_dict
-
-def str2bool(v):
-    return v.lower() in ("yes", "y", "true", "t", "1")
-
-def pil2cv(imgPIL):
-    imgCV_RGB = np.array(imgPIL, dtype = np.uint8)
-    imgCV_BGR = np.array(imgPIL)[:, :, ::-1]
-    return imgCV_BGR
-
-def cv2pil(imgCV):
-    imgCV_RGB = imgCV[:, :, ::-1]
-    imgPIL = Image.fromarray(imgCV_RGB)
-    return imgPIL
-def cv2_putChar(draw, char, x, y, fontPIL, colorRGB):
-    draw.text(xy = (x,y), text = char, fill = colorRGB, font = fontPIL)
-
-def cv2_putText_1(img, text, org, fontFace, fontScale, color):
-    min_x, max_x, min_y, max_y = org
-    
-    imgPIL = cv2pil(img)
-    draw = ImageDraw.Draw(imgPIL)
-    fontPIL = ImageFont.truetype(font = fontFace, size = fontScale)
-    if max_x - min_x >= max_y- min_y:
-        #horizontal line
-        y =  max_y
-        x = min_x
-        for char in text:
-             cv2_putChar(draw, char, x, y, fontPIL, color )
[…]

### 2020-12-08 api-exploration/kindai-ocr/translate_line.py

@@ -1,128 +1,0 @@
-import argparse
-import numpy as np
-import os
-import re
-import torch
-import time
-from utils import dataIterator, load_dict, gen_sample
-from encoder_decoder import Encoder_Decoder
-from PIL import Image, ImageDraw
-import matplotlib.pyplot as plt
-import matplotlib.patches as patches
-from PIL import Image, ImageDraw
-from scipy.misc import imread, imresize, imsave
-
-def main(model_path, dictionary_target, fea, latex, saveto, output, beam_k=5):
-    # model architecture
-    params = {}
-    params['n'] = 256
-    params['m'] = 256
-    params['dim_attention'] = 512
-    params['D'] = 684
-    params['K'] = 5748
-    params['growthRate'] = 24
-    params['reduction'] = 0.5
-    params['bottleneck'] = True
-    params['use_dropout'] = True
-    params['input_channels'] = 3
-
-    # load model
-    model = Encoder_Decoder(params)
-    model.load_state_dict(torch.load(model_path, map_location=lambda storage, loc: storage))
-    model.cuda()
-
-    # load dictionary
-    worddicts = load_dict(dictionary_target)
-    worddicts_r = [None] * len(worddicts)
-    for kk, vv in worddicts.items():
-        worddicts_r[vv] = kk
-
-    start_time = time.time()
-    channels = 1
-    folder = './kokumin/'
-    out = './kokuminOut/'
-    index = 0
-
-    # testing
-    model.eval()
-    with torch.no_grad():
-        for img_file in os.listdir(folder):
-            if  '.jpg' in  img_file:
-                label_file = folder + 'res_' + img_file.replace('jpg', 'txt')
-                if os.path.isfile(label_file) == False: continue
-                out_file = out + img_file
-                out_txtfile = out + img_file.replace('jpg', 'txt')
-                img_file = folder + img_file
-                #print img_file, label_file
-                im = imread(img_file)
-                arr = Image.fromarray(im).convert('RGB')
-                draw = ImageDraw.Draw(arr)
-   
-                #print im.shape
-                with open(label_file) as f:
-                    BBs = f.readlines()
-                BBs = [x.strip().split(',') for x in BBs]
-                f = open(out_txtfile, 'w')
-                for BB in BBs:
-                    x1 = min(int(BB[0]), int(BB[2]), int(BB[4]), int(BB[6]))
-                    y1 = min(int(BB[1]), int(BB[3]), int(BB[5]), int(BB[7]))
[…]

### 2020-12-08 api-exploration/kindai-ocr/utils.py

@@ -1,255 +1,0 @@
- #!/usr/bin/env python
-import numpy as np
-import copy
-import sys
-import pickle as pkl
-import torch
-from torch import nn
-
-# load data
-def dataIterator(feature_file, label_file, dictionary, batch_size, batch_Imagesize, maxlen, maxImagesize):
-    # offline-train.pkl
-    fp = open(feature_file, 'rb')
-    features = pkl.load(fp, encoding='latin1')
-    fp.close()
-
-    # train_caption.txt
-    fp2 = open(label_file, 'r')
-    labels = fp2.readlines()
-    fp2.close()
-
-    targets = {}
-    # map word to int with dictionary
-    for l in labels:
-        tmp = l.strip().split()
-        uid = tmp[0]
-        w_list = []
-        for w in tmp[1:]:
-            if dictionary.__contains__(w):
-                w_list.append(dictionary[w])
-            else:
-                #print('a word not in the dictionary !! sentence ', uid, 'word ', w)
-                print(w + '\t' + str(len(dictionary)))
-                dictionary[w] = len(dictionary)
-                #sys.exit()
-        targets[uid] = w_list
-
-    imageSize = {}
-    for uid, fea in features.items():
-        imageSize[uid] = fea.shape[1] * fea.shape[2]
-    # sorted by sentence length, return a list with each triple element
-    imageSize = sorted(imageSize.items(), key=lambda d: d[1])
-
-    feature_batch = []
-    label_batch = []
-    feature_total = []
-    label_total = []
-    uidList = []
-    biggest_image_size = 0
-
-    i = 0
-    for uid, size in imageSize:
-        if size > biggest_image_size:
-            biggest_image_size = size
-        fea = features[uid]
-        lab = targets[uid]
-        batch_image_size = biggest_image_size * (i + 1)
-        if len(lab) > maxlen:
-            print('sentence', uid, 'length bigger than', maxlen, 'ignore')
-        elif size > maxImagesize:
-            print(size)
-            print('image', uid, 'size bigger than', maxImagesize, 'ignore')
-        else:
-            uidList.append(uid)
-            if batch_image_size > batch_Imagesize or i == batch_size:  # a batch is full
-                feature_total.append(feature_batch)
-                label_total.append(label_batch)
-                i = 0
[…]

### 2020-12-08 scripts/api-exploration/kindai-ocr/encoder_decoder.py

@@ -1,0 +1,101 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+from encoder import DenseNet
+from decoder import Gru_cond_layer, Gru_prob
+
+
+# create gru init state
+class FcLayer(nn.Module):
+    def __init__(self, nin, nout):
+        super(FcLayer, self).__init__()
+        self.fc = nn.Linear(nin, nout)
+
+    def forward(self, x):
+        out = torch.tanh(self.fc(x))
+        return out
+
+
+# Embedding
+class My_Embedding(nn.Module):
+    def __init__(self, params):
+        super(My_Embedding, self).__init__()
+        self.embedding = nn.Embedding(params['K'], params['m'])
+        self.cuda = params['cuda']
+
+    def forward(self, params, y):
+        if y.sum() < 0.: 
+            emb = torch.zeros(1, params['m'])
+            if self.cuda:
+                emb.cuda()
+        else:
+            emb = self.embedding(y)
+            if len(emb.shape) == 3:  # only for training stage
+                emb_shifted = torch.zeros([emb.shape[0], emb.shape[1], params['m']], dtype=torch.float32)
+                if self.cuda:
+                    emb_shifted.cuda()
+                emb_shifted[1:] = emb[:-1]
+                emb = emb_shifted
+        return emb
+
+
+class Encoder_Decoder(nn.Module):
+    def __init__(self, params):
+        super(Encoder_Decoder, self).__init__()
+        self.encoder = DenseNet(growthRate=params['growthRate'], reduction=params['reduction'],
+                                bottleneck=params['bottleneck'], use_dropout=params['use_dropout'])
+        self.init_GRU_model = FcLayer(params['D'], params['n'])
+        self.emb_model = My_Embedding(params)
+        self.gru_model = Gru_cond_layer(params)
+        self.gru_prob_model = Gru_prob(params)
+        self.cuda = params['cuda']
+
+    def forward(self, params, x, x_mask, y, y_mask, one_step=False):
+        # recover permute
+        y = y.permute(1, 0)
+        y_mask = y_mask.permute(1, 0)
+
+        ctx, ctx_mask = self.encoder(x, x_mask)
+
+        # init state
+        ctx_mean = (ctx * ctx_mask[:, None, :, :]).sum(3).sum(2) / ctx_mask.sum(2).sum(1)[:, None]
+        init_state = self.init_GRU_model(ctx_mean)
+
+        # two GRU layers
[…]

### 2020-12-08 scripts/api-exploration/kindai-ocr/test.py

@@ -1,0 +1,350 @@
+"""  
+Copyright (c) 2019-present NAVER Corp.
+MIT License
+"""
+
+# -*- coding: cp932 -*-
+import sys
+import os
+import time
+import argparse
+
+import torch
+import torch.nn as nn
+import torch.backends.cudnn as cudnn
+from torch.autograd import Variable
+
+from PIL import Image, ImageDraw, ImageFont
+from utils import dataIterator, load_dict, gen_sample, load_mapping
+from encoder_decoder import Encoder_Decoder
+
+import cv2
+from skimage import io
+import numpy as np
+import craft_utils
+import imgproc
+import file_utils
+import json
+import zipfile
+import xml.etree.cElementTree as ET
+import xml.dom.minidom as minidom
+import codecs
+from craft import CRAFT
+
+from collections import OrderedDict
+def copyStateDict(state_dict):
+    if list(state_dict.keys())[0].startswith("module"):
+        start_idx = 1
+    else:
+        start_idx = 0
+    new_state_dict = OrderedDict()
+    for k, v in state_dict.items():
+        name = ".".join(k.split(".")[start_idx:])
+        new_state_dict[name] = v
+    return new_state_dict
+
+def str2bool(v):
+    return v.lower() in ("yes", "y", "true", "t", "1")
+
+def pil2cv(imgPIL):
+    imgCV_RGB = np.array(imgPIL, dtype = np.uint8)
+    imgCV_BGR = np.array(imgPIL)[:, :, ::-1]
+    return imgCV_BGR
+
+def cv2pil(imgCV):
+    imgCV_RGB = imgCV[:, :, ::-1]
+    imgPIL = Image.fromarray(imgCV_RGB)
+    return imgPIL
+def cv2_putChar(draw, char, x, y, fontPIL, colorRGB):
+    draw.text(xy = (x,y), text = char, fill = colorRGB, font = fontPIL)
+
+def cv2_putText_1(img, text, org, fontFace, fontScale, color):
+    min_x, max_x, min_y, max_y = org
+    
+    imgPIL = cv2pil(img)
+    draw = ImageDraw.Draw(imgPIL)
+    fontPIL = ImageFont.truetype(font = fontFace, size = fontScale)
+    if max_x - min_x >= max_y- min_y:
+        #horizontal line
+        y =  max_y
+        x = min_x
+        for char in text:
+             cv2_putChar(draw, char, x, y, fontPIL, color )
[…]

### 2020-12-08 scripts/api-exploration/kindai-ocr/utils.py

@@ -1,0 +1,255 @@
+ #!/usr/bin/env python
+import numpy as np
+import copy
+import sys
+import pickle as pkl
+import torch
+from torch import nn
+
+# load data
+def dataIterator(feature_file, label_file, dictionary, batch_size, batch_Imagesize, maxlen, maxImagesize):
+    # offline-train.pkl
+    fp = open(feature_file, 'rb')
+    features = pkl.load(fp, encoding='latin1')
+    fp.close()
+
+    # train_caption.txt
+    fp2 = open(label_file, 'r')
+    labels = fp2.readlines()
+    fp2.close()
+
+    targets = {}
+    # map word to int with dictionary
+    for l in labels:
+        tmp = l.strip().split()
+        uid = tmp[0]
+        w_list = []
+        for w in tmp[1:]:
+            if dictionary.__contains__(w):
+                w_list.append(dictionary[w])
+            else:
+                #print('a word not in the dictionary !! sentence ', uid, 'word ', w)
+                print(w + '\t' + str(len(dictionary)))
+                dictionary[w] = len(dictionary)
+                #sys.exit()
+        targets[uid] = w_list
+
+    imageSize = {}
+    for uid, fea in features.items():
+        imageSize[uid] = fea.shape[1] * fea.shape[2]
+    # sorted by sentence length, return a list with each triple element
+    imageSize = sorted(imageSize.items(), key=lambda d: d[1])
+
+    feature_batch = []
+    label_batch = []
+    feature_total = []
+    label_total = []
+    uidList = []
+    biggest_image_size = 0
+
+    i = 0
+    for uid, size in imageSize:
+        if size > biggest_image_size:
+            biggest_image_size = size
+        fea = features[uid]
+        lab = targets[uid]
+        batch_image_size = biggest_image_size * (i + 1)
+        if len(lab) > maxlen:
+            print('sentence', uid, 'length bigger than', maxlen, 'ignore')
+        elif size > maxImagesize:
+            print(size)
+            print('image', uid, 'size bigger than', maxImagesize, 'ignore')
+        else:
+            uidList.append(uid)
+            if batch_image_size > batch_Imagesize or i == batch_size:  # a batch is full
+                feature_total.append(feature_batch)
+                label_total.append(label_batch)
+                i = 0
[…]

### 2020-12-09 outputs/documents/paper.Rmd
Begin updating paper

@@
 output:
-  pdf_document:
+  bookdown::pdf_document2:
+    citation_package: natbib
+    keep_tex: false
+    fig_caption: true
+    number_sections: true
     latex_engine: xelatex
-  html_document: default
+    toc: false
 bibliography: references.bib
@@
 ```{r echo=FALSE, include=FALSE, warning=FALSE}
-library("reticulate")
+library(reticulate)
+library(tidyverse)
 ```
@@
 This step involves tools and methods to collect raw data in an systematic way.
-In this paper we are interested in gathering data from Portable Document Format (PDF) files, in particular, when these PDFs were created by scans, and hence must be processed before their data can be analysed.
-Such PDF files are unstructured data, meaning that the data are not tagged and are not organised in a regular way.^[Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset.
+In this paper we are interested in gathering data from Portable Document Format (PDF) files, in particular, when these PDFs were created by scans, and hence must be processed before the data they contain can be prepared, cleaned, and analysed.
+Such PDF files are generally unstructured data, meaning that the data are not tagged nor organised in a regular way.^[Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset.
 Some examples are tables and relations.
@@
 However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data [@Losee2006].
-This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags could be assigned manually, typically a statistical model is used for reasons of efficiency, and this process is called Optical Character Recognition (OCR).
-We evaluate several pre-trained commercial OCR options accessed via APIs: 1) X, 2), and 3), ; additionally several OCR options that are run locally: 4) X, 5), and 6), ; and finally 7) training our own model.
+This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags in the form of a text replacement for each character image could be assigned manually, typically a statistical model is used for reasons of efficiency and reproducibility, and this process is called Optical Character Recognition (OCR).
+We evaluate several pre-trained commercial OCR options accessed via APIs: 1) X, 2), Y and 3) Z; additionally several pre-trained OCR options that we run ourselves: 4) X, 5), Y and 6) Z ; and finally 7) training and running our own model.
 We find...
@@
 
-PDF files were developed in 1993 by the technology company Adobe and are useful for documents because they should display in a consistent way independent of the environment that created them or the environment in which they are being viewed.
+PDF files were developed in 1993 by the technology company Adobe and are useful for documents because they are meant to display in a consistent way independent of the environment that created them or the environment in which they are being viewed.
+A PDF viewed on an iPhone should look the same as on a Android phone, as on a Linux desktop.
 One feature of PDFs is that they can include a variety of objects, for instance, text, photos, figures, etc.
@@
 This is more likely when the PDF only contains simple text or regular tables.
-In particular, if the PDF has been created by an application such as Word then often the text can be extracted in this way because they are stored as text.
-But it is not as easy if the text has been stored as an image which is then part of the PDF
+In particular, if the PDF has been created by an application such as Microsoft Word, or another document or form creation system, then often the text data can be extracted in this way because they are actually stored as text within the PDF.
+But it is not as easy if the text has been stored as an image which is then part of the PDF.
+This may be the case for PDFs produced through scans or photos of physical documents, and some older document preparation software.
 
-Furthermore, there is a linguistic component that adds more complexity.
-For instance, it is well known that non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[ADD CITE]**.
-It is because those characters have complicated structures, a large number of categories (for instance, compare the 26 characters in the English alphabet with the thousands of characters in Japanese kanji), and resemblance among characters, font unevenness, or writing styles.
-In those cases, the need for reliable tools or methods with the ability to elicit data becomes extremely important.
+**[DIEGO - where is this coming from?]** Furthermore, there is a linguistic component that adds more complexity.
+For instance, non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[DIEGO - add cite]**.
+Not only do these languages have complicated structures and a large number of categories (for instance, compare the 26 characters in the English alphabet with the thousands of characters in Japanese kanji).
+But often many characters are similar and fonts may have a large effect **[DIEGO - add cite]**.
+In those cases, the need for reliable approaches to replace an image containing many characters with text of those characters becomes important.
 
-Optical character recognition (OCR),is a process that transforms a bitmapped image of printed or handwritten text into text code **[ADD CITE]**.
-It thereby becomes machine-readable.
-It has been used to parse images of characters since the 1950s **[ADD CITE]**.
-These initial approaches used mechanical and optical means of rotating disks and photomultiplier flying spot scanner with a cathode ray tube lens, followed by photocells and arrays of them **[ADD CITE]**.
-The OCR process was slow, and one line of characters could be digitized at a time.
-These days once a printed or handwritten text has been captured optically by a scanner or some other optical means, the digital image goes through the following stages of a computer recognition system [@Cheriet2007]:
+Optical character recognition (OCR) is a process that transforms a image of text into actual text.
+Although there may not be much difference to a human reading a PDF before and after OCR, the main difference is that the PDF is now machine-readable **[DIEGO - add cite]**.
+OCR has been used to parse images of characters since the 1950s, initially using physical processes **[DIEGO - add cite]**.
+Such approaches were understandably slow and have been replaced by a computer-based recognition system involving the following steps [@Cheriet2007 p.
+X]:
 
-- The preprocessing stage that enhances the quality of the input image and locates
-the data of interest.
-- The feature extraction stage that captures the distinctive characteristics of the
-digitized characters for recognition.
-- The classification stage that processes the feature vectors to identify the characters and words.
+- Pre-processing to both: increase the quality of the input image, and to focus on the data of interest.
+- Feature extraction to identify the distinctive features of the characters to be recognized.
+- The actual classification stage, in which those features are used to identify the characters.
 
-In this paper we review various OCR options for researchers who need to gather data from PDFs in which the text must be extracted to be reused, edited, or reformatted; the text should be available for full-text information retrieval; the text is to be coded in HTML or SGML; the text should be available to adaptive equipment for the visually impaired; the file size is of concern (in terms of storage or bandwidth to transmit); or the resources are available to perform OCR and correct the output.
+In this paper we review various OCR options for data analysts who need to gather their data from PDFs where the characters of interest for analysis must first be transformed from image to text.
+The paper goes through the process of using various options to do this OCR and the tradeoffs that must be made.
+We consider a few different options in terms of the image that is to be transformed.
+We start with a one page extract of modern English, a one-page table of numbers, one page of modern Japanese, one page from an English book from the 1800s, and a page from a Japanese dictionary from the early 1900s.
 
-Although this step remains the same regardless of the field of study, the methods used vary between those fields of study because of their different interests.
-Moreover, the diversity of data types adds complexity to the process of gathering data.
+We find... **[TBD]**.
 
-**When they consider a primer on what OCR options exist these days depending on your technical ability and then how they perform for an easy example and then how they perform for a hard example (the Japanese extract) and finally some suggestions for what is needed in the future....**
+The remainder of this paper is structured as follows... **[TBD]**. Finally we make some suggestions for what is needed in the future.
 
-**Our paper represents...**
+**DIEGO - what is this?**.
+; the text should be available for full-text information retrieval; the text is to be coded in HTML or SGML; the text should be available to adaptive equipment for the visually impaired; the file size is of concern (in terms of storage or bandwidth to transmit); or the resources are available to perform OCR and correct the output.
 
-**The remainder of this paper is structured as follows...**
+# Background
+
+In this section we introduce the OCR options that we consider, they essential features and cost.
+
+There are seven OCR options evaluated in this study (Table \@ref(tab:tableofoptions)).
+
+```{r tableofoptions, echo=FALSE, warning = FALSE, message = FALSE}
+options <- read_csv(here::here("inputs/ocr_options.csv"))
+options %>% 
+  knitr::kable(booktabs = TRUE, 
+               caption = "OCR options",
+               )
+
+```
+
+**Add paragraph about each.**
 
@@
 
-## Test Samples
+## Modern English
 
-Japanese dictionaries...[Rohan]
+**TBD.**
+
+## Table of numbers
+
+**TBD.**
+
+## Modern Japanese
+
+**TBD.**
+
+## English book from the 1800s
+
+**TBD.**
+
+## Japanese dictionaries from the early 1900s
 
@@
 Words in English were counted as one character for this analysis.
-MOreover, the sample text was divided into four images called **sections** as illustrated in Figure \@ref(fig:sections).
+Moreover, the sample text was divided into four images called **sections** as illustrated in Figure \@ref(fig:sections).
 These new images were assessed across all OCR tools.
@@
 This is important since it is expected to obtain from each OCR tool the correct sequence of characters.
-For instance, from section 1 in figure xx, the first five characters from the first line are **[一本の傘を]**.
+For instance, from section 1 in Figure \@ref(fig:section1), the first five characters from the first line are **[一本の傘を]**.
 We expect to see the same sequence from each OCR tool.
@@
 
-## OCR options
-
-The following list contains the OCR APIs and libraries available that will be evaluated in this study:
-
-| OCR Tool                             | Company	 | Type           |	Monthly Price Aug/2020 |	Tech Requierements |
-| ------------------------------------ | --------- | -------------- | ------- | ------------------ |
-| Azure Cognitive Services (OCR)       | Microsoft | API		        | Free Web Container: 5000/Free; <br/> <br/> S1 Web Container: 0-1M/$1.50 per 1,000 trans, 1M-5M/$1 per 1,000 trans, 5M-10M/$0.65 per 1,000 trans, 10M-100M/$0.65 per 1,000 trans, +100M/$0.65 per 1,000 trans        |                    |
-| Amazon Rekognition	                 | Amazon	   | API		        | First 1 million images: $0.001 per image <br/> <br/> Next 9 million images $0.0008 per image <br/> <br/> Next 90 million images $0.0006 per image <br/> <br/> Over 100 million images $0.0004 per image         |                    |
-| PyTesseract (Wrapper Google's OCR Engine)    |           | Python Library | Free    |                    |
-Standard: $0.002 per trans      |                    |
-| Kraken	(Linux OS)                   |           | Python Library	| Free	  |                    |
-| Google Vision (for Text recognition) | Google	   | API		        | 1000/Free, 5 mill/$1.5, >5mill/$0.6        |                    |
-| Amazon Textract	                     | Amazon	   | API		        | First 1 Million pages: $0.015 - $0.05 per page, <br/> <br/> Over 1 Million pages: $0.01 - $0.04 per page        |                    |
-|	Kindai-OCR                           | Result of n2i Project    | Python Library | Free    |                    |
+# Results
 

### 2020-12-12 outputs/documents/paper.Rmd
Add abstract and high-level descriptions of kindai and tesseract

@@
 ---
-title: "Notes and approaches to OCR"
-author: "Rohan Alexander, John Tang, Diego Mamanche Castellanos"
-date: "8 December 2020"
-abstract: "TBD"
+title: "Using Optical Character Recognition in an Applied Research Workflow"
+author:
+  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
+  - John Tang^[University of Melbourne.]
+  - Diego Mamanche Castellanos^[University of Toronto.]
+date: "12 December 2020"
+abstract: "We discuss the use of Optical Character Recognition (OCR) as a initial step in an applied research workflow.
+OCR is a way of converting images, for instance in a PDF file, into text and numbers that can then be analysed.
+We review a variety of methods and their relative merit.
+The choice between these approaches turns on the scale of the OCR required, the level of funding that is available, and the user's technical skills.
+We provide a hueristic to guide this decision and worked examples.
+Finally, we place this within the context of an illustrative applied research workflow detailing its relationship with other aspects of the workflow."
 output:
@@
 This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags in the form of a text replacement for each character image could be assigned manually, typically a statistical model is used for reasons of efficiency and reproducibility, and this process is called Optical Character Recognition (OCR).
-We evaluate several pre-trained commercial OCR options accessed via APIs: 1) X, 2), Y and 3) Z; additionally several pre-trained OCR options that we run ourselves: 4) X, 5), Y and 6) Z ; and finally 7) training and running our own model.
+We evaluate several pre-trained commercial OCR options accessed via APIs: 1) **X**, 2) **Y**, and 3) **Z**; additionally several pre-trained OCR options that we run ourselves: 4) **X**, 5) **Y**, and 6) **Z**; and finally 7) training and running our own model.
 We find...
@@
 
+Our paper is similar to @Rychlik2020 which focuses on Pashto, Farsi, and Traditional Chinese.
+
 The remainder of this paper is structured as follows... **[TBD]**. Finally we make some suggestions for what is needed in the future.
-
-**DIEGO - what is this?**.
-; the text should be available for full-text information retrieval; the text is to be coded in HTML or SGML; the text should be available to adaptive equipment for the visually impaired; the file size is of concern (in terms of storage or bandwidth to transmit); or the resources are available to perform OCR and correct the output.
 
@@
 
-In this section we introduce the OCR options that we consider, they essential features and cost.
-
-There are seven OCR options evaluated in this study (Table \@ref(tab:tableofoptions)).
+In this section we introduce the OCR options that we consider, their essential features, and cost. There are **seven** OCR options evaluated in this study (Table \@ref(tab:tableofoptions)).
 
@@
 
-**Add paragraph about each.**
+Amazon Rekognition is a proprietary
+
+Amazon Textract
+
+Azure Cognitive Services
+
+Google Vision
+
+Kindai OCR [@Le2019] - https://github.com/ducanh841988/Kindai-OCR - is a pre-trained model that uses an attention based encoder-decoder approach specifically designed for Japanese historical documents.
+It is part of a larger research program on Japanese character recognition including @Horiuchi2009 and @Nguyen2017.
+This research program is complementary to research on historical Hanja (Korean) documents, for instance @Kim2004, and  historical Khmer (Cambodia) documents, for instance @Valy2020.
+@Le2019b provides broader consideration of issues with the recognition of historical Japanese, and related, characters including 'noised, damaged characters, and background', as well as the possibility that characters may be 'written in cursive and are connected'.
+The Center for Open Data in the Humanities - http://codh.rois.ac.jp - provides a large number of training datasets, and runs the n2i Project from which Kindai came out of.
+@Narang2020 provides an overview.
+
+Kraken
+
+Tesseract **[ADD CITE]** - https://github.com/tesseract-ocr/tesseract - is an open-source OCR engine initially developed 'at HP between 1985 and 1995, shelved for 10 years, open-sources in 2006 and now developed mostly at Google' [@Smith2013].
+It has had a variety of versions, with the latest being Tesseract 4 which added a 'neural net (LSTM) based OCR engine' [@tesseract2018].
+Tesseract is a widely used OCR engine with a variety of implementations available including the default usage of command line, Python through the pytesseract package **[ADD CITE]** and R through the tesseract package [@Ooms2019] for which a useful starter example is @Rodrigues2019.
+
+There are two additional approaches that researchers may also consider: manual and roll-your-own.
+In the manual approach, teams of research assistants are paid to inspect each page and input the correct element.
+This is likely the gold-standard in terms of accuracy, however it is only approach for smaller datasets, and is not reproducible.
+Finally, as the statistics underlying the approaches mentioned above are within the capacity of many researchers it is tempting to conclude that one should write one's own OCR engine.
+Don't do this.
 
@@
 
-# References
-
 1: https://www.researchgate.net/publication/267465115_An_Overview_and_Applications_of_Optical_Character_Recognition
@@
 2: https://books-scholarsportal-info.myaccess.library.utoronto.ca/en/read?id=/ebooks/ebooks2/wiley/2011-12-13/1/9780470176535
-
-3:
 
@@
 
-12: Anh Duc Le, Daichi Mochihashi, Katsuya Masuda, Hideki Mima, and Nam Tuan Ly.
-2019.
-Recognition of Japanese historical text lines by an attention-based encoder-decoder and text line generation.
-In Proceedings of the 5th International Workshop on Historical Document Imaging and Processing (HIP ’19).
-Association for Computing Machinery, New York, NY, USA, 37–41.
-DOI:https://doi.org/10.1145/3352631.3352641
+# References

### 2020-12-12 outputs/documents/paper.Rmd
Add abbyy to paper and add some missing lit

@@
   bookdown::pdf_document2:
-    citation_package: natbib
     keep_tex: false
@@
 This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags in the form of a text replacement for each character image could be assigned manually, typically a statistical model is used for reasons of efficiency and reproducibility, and this process is called Optical Character Recognition (OCR).
-We evaluate several pre-trained commercial OCR options accessed via APIs: 1) **X**, 2) **Y**, and 3) **Z**; additionally several pre-trained OCR options that we run ourselves: 4) **X**, 5) **Y**, and 6) **Z**; and finally 7) training and running our own model.
+We evaluate several pre-trained commercial OCR options accessed through proprietary APIs: 1) Abbyy, 2) Amazon Rekognition, 3) Amazon Textract, 4) Azure Cognitive Services, and 5) Google Vision; additionally several pre-trained and trainable OCR options that a user runs themselves: 6) Kindai OCR, 7) Kraken, and finally 8) Tesseract.
 We find...
@@
 
-Our paper is similar to @Rychlik2020 which focuses on Pashto, Farsi, and Traditional Chinese.
+Our paper is similar to @Rychlik2020 which focuses on Pashto, Farsi, and Traditional Chinese. Additional useful surveys include @Lombardi2020 and @Reul2019.
 
@@
 
+Abbyy
+
 Amazon Rekognition is a proprietary
@@
 The Center for Open Data in the Humanities - http://codh.rois.ac.jp - provides a large number of training datasets, and runs the n2i Project from which Kindai came out of.
-@Narang2020 provides an overview.
 
-Kraken
+OCRopus **[ADD CITE]** - https://github.com/ocropus/ocropy - is an open-source OCR engine initially developed in 2007 as 'a Google-sponsored project' [@Breuel2007].
+Kraken **[ADD CITE]** - https://github.com/mittagessen/kraken - is an 'extensively rewritten fork of the OCRopus system' by Benjamin Kiessling [@Kiessling2019].
+@Martinek2020 use Kraken to create 'an efficient domain-dependent OCR system that focuses on historical German documents by picking the best tools and approaches available'.
+Similarly, @Romanov2017 use Kraken to achieve 'accuracy rates for classical Arabic-script texts in the high nineties'.
 
@@
 
-10: http://codh.rois.ac.jp/software/kindai-ocr/
-
-11: https://github.com/ducanh841988/Kindai-OCR
+\newpage
 

### 2020-12-13 outputs/documents/paper.Rmd
Citations update

@@
 
-**[DIEGO - where is this coming from?]** Furthermore, there is a linguistic component that adds more complexity.
-For instance, non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[DIEGO - add cite]**.
+**[The ideas for this paragraph are coming from K.Karthick, K.B.Ravindrakumar, R.Francis, S.Ilankannan = Steps Involved in Text Recognition and Recent Research in OCR.
+Preprocessing/Factors Affecting the Text Recognition Quality, Chinese Character Recognition, and Arabic Character Recognition as Japanese shared several similarities with Chinese such as Kanji.
+It is in references folder as F2670037619.pdf]** Furthermore, there is a linguistic component that adds more complexity.
+For instance, non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[DIEGO - add cite = same as above]**.
 Not only do these languages have complicated structures and a large number of categories (for instance, compare the 26 characters in the English alphabet with the thousands of characters in Japanese kanji).
-But often many characters are similar and fonts may have a large effect **[DIEGO - add cite]**.
+But often many characters are similar and fonts may have a large effect **[DIEGO - add cite = same as above]**.
 In those cases, the need for reliable approaches to replace an image containing many characters with text of those characters becomes important.
@@
 Optical character recognition (OCR) is a process that transforms a image of text into actual text.
-Although there may not be much difference to a human reading a PDF before and after OCR, the main difference is that the PDF is now machine-readable **[DIEGO - add cite]**.
-OCR has been used to parse images of characters since the 1950s, initially using physical processes **[DIEGO - add cite]**.
+Although there may not be much difference to a human reading a PDF before and after OCR, the main difference is that the PDF is now machine-readable **[This paragraph is comming from Cheriet2007 p.
+X, Character Recognition Systems: A Guide for Students and Practioners, Chapter 1.
+It is in references folder as 2007+Character_Recognitio+Pages=[1-4].pdf]**.
+OCR has been used to parse images of characters since the 1950s, initially using physical processes **[Same as the previous one]**.
 Such approaches were understandably slow and have been replaced by a computer-based recognition system involving the following steps [@Cheriet2007 p.

### 2020-12-14 outputs/documents/paper.Rmd
Clean up intro and folders and description of japanese dictionary

--- 2020-12-12 outputs/documents/paper.Rmd
@@
   - Diego Mamanche Castellanos^[University of Toronto.]
-date: "12 December 2020"
+date: "14 December 2020"
 abstract: "We discuss the use of Optical Character Recognition (OCR) as a initial step in an applied research workflow.
@@
     toc: false
+spacing: single
 bibliography: references.bib
@@
 This may be the case for PDFs produced through scans or photos of physical documents, and some older document preparation software.
-
-**[DIEGO - where is this coming from?]** Furthermore, there is a linguistic component that adds more complexity.
-For instance, non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[DIEGO - add cite]**.
+Furthermore, there is a linguistic component that adds more complexity [@Kanagarathinam2019].
+For instance, non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process.
 Not only do these languages have complicated structures and a large number of categories (for instance, compare the 26 characters in the English alphabet with the thousands of characters in Japanese kanji).
-But often many characters are similar and fonts may have a large effect **[DIEGO - add cite]**.
+But often many characters are similar and fonts may have a large effect.
 In those cases, the need for reliable approaches to replace an image containing many characters with text of those characters becomes important.
@@
 Optical character recognition (OCR) is a process that transforms a image of text into actual text.
-Although there may not be much difference to a human reading a PDF before and after OCR, the main difference is that the PDF is now machine-readable **[DIEGO - add cite]**.
-OCR has been used to parse images of characters since the 1950s, initially using physical processes **[DIEGO - add cite]**.
+Although there may not be much difference to a human reading a PDF before and after OCR, the main difference is that the PDF is now machine-readable [@Cheriet2007].
+OCR has been used to parse images of characters since the 1950s, initially using physical processes.
 Such approaches were understandably slow and have been replaced by a computer-based recognition system involving the following steps [@Cheriet2007 p.
-X]:
+4]:
 
@@
 
-In this section we introduce the OCR options that we consider, their essential features, and cost. There are **seven** OCR options evaluated in this study (Table \@ref(tab:tableofoptions)).
+In this section we introduce the OCR options that we consider, their essential features, and cost.
+There are **eight** **[UPDATE]** OCR options evaluated in this study (Table \@ref(tab:tableofoptions)).
 
@@
 ```
+
+The gold-standard in terms of quality is a manual approach.
+For instance, a team of research assistants who were paid to inspect each page, inputting the correct element and checking the inputs of others will likely provide the best recognition.
+While this option is only possible for smaller datasets and is not reproducible, sharing high-quality datasets created in this way is important for evaluating the output of automated approaches.
 
@@
 
-OCRopus **[ADD CITE]** - https://github.com/ocropus/ocropy - is an open-source OCR engine initially developed in 2007 as 'a Google-sponsored project' [@Breuel2007].
-Kraken **[ADD CITE]** - https://github.com/mittagessen/kraken - is an 'extensively rewritten fork of the OCRopus system' by Benjamin Kiessling [@Kiessling2019].
+OCRopus - https://github.com/ocropus/ocropy - is an open-source OCR engine initially developed in 2007 as 'a Google-sponsored project' [@Breuel2007].
+Kraken - https://github.com/mittagessen/kraken - is an 'extensively rewritten fork of the OCRopus system' by Benjamin Kiessling [@Kiessling2019].
 @Martinek2020 use Kraken to create 'an efficient domain-dependent OCR system that focuses on historical German documents by picking the best tools and approaches available'.
@@
 
-Tesseract **[ADD CITE]** - https://github.com/tesseract-ocr/tesseract - is an open-source OCR engine initially developed 'at HP between 1985 and 1995, shelved for 10 years, open-sources in 2006 and now developed mostly at Google' [@Smith2013].
+Tesseract - https://github.com/tesseract-ocr/tesseract - is an open-source OCR engine initially developed 'at HP between 1985 and 1995, shelved for 10 years, open-sources in 2006 and now developed mostly at Google' [@Smith2013].
 It has had a variety of versions, with the latest being Tesseract 4 which added a 'neural net (LSTM) based OCR engine' [@tesseract2018].
@@
 
-There are two additional approaches that researchers may also consider: manual and roll-your-own.
-In the manual approach, teams of research assistants are paid to inspect each page and input the correct element.
-This is likely the gold-standard in terms of accuracy, however it is only approach for smaller datasets, and is not reproducible.
-Finally, as the statistics underlying the approaches mentioned above are within the capacity of many researchers it is tempting to conclude that one should write one's own OCR engine.
-Don't do this.
-
 # Data
 
-## Modern English
+## Book in English
 
@@
 
+A common reason for wanting to 
 **TBD.**
@@
 
-## English book from the 1800s
-
-**TBD.**
-
 ## Japanese dictionaries from the early 1900s
 
-For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the selected OCR tools.
-The image contains 3293 characters.
-Words in English were counted as one character for this analysis.
-Moreover, the sample text was divided into four images called **sections** as illustrated in Figure \@ref(fig:sections).
-These new images were assessed across all OCR tools.
+**[JOHN: Add a para about the origin of this dictionary.]**
 
-```{r sections, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
-knitr::include_graphics(here::here("outputs/documents/sections.png"))
+Here we focus on a page focused on 'a', which is あ in hiragana or ア in katakana Figure \@ref(fig:japanesedictionaryfirstpage).
+
+```{r japanesedictionaryfirstpage, echo=FALSE, fig.cap="A page from an early 1900s Japanese dictionary.", out.width = '90%', fig.align="center"}
+knitr::include_graphics(here::here("inputs/japanese_dictionaries/sample_page.png"))
 ```
 
-This example is in a vertical form, meaning that it should be read it from right to left and from the top to the bottom.
-This is important since it is expected to obtain from each OCR tool the correct sequence of characters.
-For instance, from section 1 in Figure \@ref(fig:section1), the first five characters from the first line are **[一本の傘を]**.
-We expect to see the same sequence from each OCR tool.
-
-The following figures corresponds to each section extracted from the sample:
-
-```{r section1, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
-knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_1.png"))
-```
-
-```{r section2, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
-knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_2.png"))
-```
-
-```{r section3, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
-knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_3.png"))
-```
-
-```{r section4, echo=FALSE, fig.cap="UPDATE CAPTION", out.width = '90%'}
-knitr::include_graphics(here::here("inputs/cropped_pages/00-sample_pages_3_sec_4.png"))
-```
+This page has several features of interest.
+Firstly, it is in vertical form and should be read from right to left.
+This means that the first five characters that we expect from an OCR output are: 一本の傘を.
+The page is divided into four rows of content.
+An OCR workflow will need to take this into account during the pre-processing stage.
+In total, this page contains 3,293 characters, and while a majority of them are Japanese, there are still 99 English characters.
+Finally, there are also important nuances in terms of punctuation.
+For instance, certain types of brackets - **[ADD AN EXAMPLE]** - contain the origin of the word.
 

### 2020-12-15 outputs/documents/paper.Rmd
Update all background and add the three examples

@@
 In this paper we are interested in gathering data from Portable Document Format (PDF) files, in particular, when these PDFs were created by scans, and hence must be processed before the data they contain can be prepared, cleaned, and analysed.
-Such PDF files are generally unstructured data, meaning that the data are not tagged nor organised in a regular way.^[Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset.
-Some examples are tables and relations.
-Semi-structured data contains this same information, but instead of having regular structures applied to all items in the dataset, the data might be interpreted with structural information.
-It can be supplied as tags e.g.
-name = "Bob" but also other markers to separate semantic elements and enforce hierarchies of records and fields within the data.
-Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags.
-However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data [@Losee2006].
-This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags in the form of a text replacement for each character image could be assigned manually, typically a statistical model is used for reasons of efficiency and reproducibility, and this process is called Optical Character Recognition (OCR).
-We evaluate several pre-trained commercial OCR options accessed through proprietary APIs: 1) Abbyy, 2) Amazon Rekognition, 3) Amazon Textract, 4) Azure Cognitive Services, and 5) Google Vision; additionally several pre-trained and trainable OCR options that a user runs themselves: 6) Kindai OCR, 7) Kraken, and finally 8) Tesseract.
+Such PDF files are generally unstructured data, meaning that the data are not tagged nor organised in a regular way.^[@Losee2006 describes how structured data have a highly-regular organization or a there is some pre-defined data model where regularities apply to everything in a dataset, for instance a table.
+@Losee2006 further describes how semi-structured data contains this same information, but instead of a regular structure that applies to the entire dataset, there may be some structural information, for instance, tags such as 'name = "Bob"', or some other marker.
+Finally, unstructured data, such as texts or images, holds information with no explicit structured data.
+However, tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data.
+The diversity of possible data structures complicates the data gathering process as each may need a specific approach.] While tags in the form of a text replacement for each character image could be assigned manually, typically a statistical model is used for reasons of efficiency and reproducibility, and this process is called Optical Character Recognition (OCR).
+We evaluate several pre-trained commercial OCR options accessed through proprietary APIs: 1) Abbyy, 2) Amazon Textract, 3) Azure Cognitive Services, and 4) Google Vision; additionally several pre-trained and trainable OCR options that a user runs themselves: 5) Kindai OCR, 6) Kraken, and finally 7) Tesseract.
 We find...
@@
 In this section we introduce the OCR options that we consider, their essential features, and cost.
-There are **eight** **[UPDATE]** OCR options evaluated in this study (Table \@ref(tab:tableofoptions)).
+There are **seven** **[UPDATE]** OCR options evaluated in detail in this study (Table \@ref(tab:tableofoptions)).
 
@@
                caption = "OCR options",
+               linesep = ""
                )
@@
 
-Abbyy
+ABBYY - https://www.abbyy.com - is a private company that has conducted OCR through the product FineReader since 1993.
+FineReader has a variety of options that can be useful.There are a variety of options in terms of using FineReader including downloading an application locally, accessing it online, or using an iPhone app.
+The iPhone app can be especially useful when the item that is being scanned should not have its pages separated or even be fully flattened for scanning because it uses the camera.
+FineReader is capable of manual 'training' for instance, a user is able to identify unrecognised items.
+There are a variety of different prices depending on the application.
+FineReader online requires an annual subscription that allows for 5,000 pages for \$149 (USD), FineReader for Mac is \$150 (CAD).
 
-Amazon Rekognition is a proprietary
+Amazon Textract - https://aws.amazon.com/textract/ - is an OCR application that is available through the Amazon.
+It can be accessed via an API or through Amazon Web Services (AWS).
+Textract is limited to only English for handwriting and even the printed text languages that Textract can detect are limited to English, Spanish, Italian, French, Portuguese and German [@amazontextractwebsite].
+Helpfully, the output can be put into a workflow such that low confidence recognitions can be automatically reviewed by a human.
+Textract requires a subscription and on a monthly basis the cost begins at \$1.50 per 1,000 pages for documents with text, and \$15.00 for documents with tables.
 
-Amazon Textract
+Microsoft Azure Cognitive Services provides OCR through the Computer Vision application - https://azure.microsoft.com/en-us/services/cognitive-services/computer-vision/ [@citeazuredocs].
+It is access via an API and handwriting OCR is only available for English, however printed OCR is available for a wide variety of languages including more complicated languages such as Arabic, Chinese, and Japanese.
+Mixed languages are also possible.
+The cost to use the API begins at \$1.50 per 1,000 pages.
 
-Azure Cognitive Services
-
-Google Vision
+Google Vision API - https://cloud.google.com/vision - is an OCR application for a wide variety of printed languages including those of Azure.
+It is available through an API.
+The cost to use the API begins at \$1.50 per 1,000 pages [@citegooglevision].
 
@@
 It has had a variety of versions, with the latest being Tesseract 4 which added a 'neural net (LSTM) based OCR engine' [@tesseract2018].
-Tesseract is a widely used OCR engine with a variety of implementations available including the default usage of command line, Python through the pytesseract package **[ADD CITE]** and R through the tesseract package [@Ooms2019] for which a useful starter example is @Rodrigues2019.
+Tesseract is a widely used OCR engine with a variety of implementations available including the default usage of command line, Python through the pytesseract package **[ADD CITE]** and R through the Tesseract package [@Ooms2019] for which a useful starter example is @Rodrigues2019.
+
+There are various other options that we considered, but ultimately did not evaluate in a serious way.
+The first of this is Amazon Rekognition - https://aws.amazon.com/rekognition/ - which is a **[ADD description]**.
+However, the service only recognizes up to 50 characters per image.
+As this is too small for most OCR applications in academia we did not further explore this service.
 
@@
 
-**TBD.**
+We may be interested in the text from a book itself.
+In that circumstance, we'd often have scans of pages of each book, for instance as illustrated in Figure \@ref(fig:janeeyre) illustrates a page containing a table from @Bronte1847.
+
+```{r janeeyre, echo=FALSE, fig.cap="A scanned page from a book.", out.width = '70%', fig.align="center"}
+knitr::include_graphics(here::here("inputs/jane_eyre/sample_page.png"))
+```
+
+Scanned pages of text from books will typically have some different fonts that need to be considered.
+They may also have page numbers and illustrations.
+Finally they may have various Pages of text Tables typically have several interesting features with regard to OCR.
+They typically have a page number and a title, both of which may or may not be important.
+They are then typically arranged in ordered rows and columns, which may or may not have lines separating them.
+Some of the cells may have symbols in them that may relate to footnotes at the end of the table.
+And finally, they may have additional comments and notes at the end of the table.
 
@@
 
-A common reason for wanting to 
-**TBD.**
+A common reason for wanting to OCR a document is to use the tables that are contained in old books. Figure \@ref(fig:bowleytable) illustrates a page containing a table from @Bowley1902
 
-## Modern Japanese
+```{r bowleytable, echo=FALSE, fig.cap="A scanned table from a book.", out.width = '80%', fig.align="center"}
+knitr::include_graphics(here::here("inputs/bowley/sample_table.png"))
+```
 
-**TBD.**
+Tables typically have several interesting features with regard to OCR.
+They typically have a page number and a title, both of which may or may not be important.
+They are then typically arranged in ordered rows and columns, which may or may not have lines separating them.
+Some of the cells may have symbols in them that may relate to footnotes at the end of the table.
+And finally, they may have additional comments and notes at the end of the table.
 
@@
 
-## Azure Corgnitive Services - Computer Vision OCR
+## Azure Cognitive Services - Computer Vision OCR
 
@@
 
-In python we need several libraries for calling the API.
+In Python we need several libraries for calling the API.
 
@@
 
-# Other limitations
+### Other limitations
 
@@
 https://aws.amazon.com/textract/faqs/
-
-## Amazon Rekognition
-
-According to Amazon's website, Amazon Rekognition supports text in most Latin scripts and numbers.
-Text detection recognizes up to 50 sequences of characters per the image or video frame and lists them as words and lines.
-
-https://aws.amazon.com/rekognition/faqs/
 
